Magnesium isoglycyrrhizinate alleviates alcohol-associated liver disease through targeting HSD11B1

Version 1

Abstract

While magnesium isoglycyrrhizinate (MgIG) is a clinically approved therapy for alcohol-associated liver disease (ALD), its precise molecular targets and mechanisms remain uncharacterized. This study aimed to define MgIG’s hepatoprotective actions in chronic-binge ALD mouse models and ethanol/palmitic acid-exposed AML-12 hepatocytes. Through an integrated strategy encompassing RNA sequencing, molecular docking, and microscale thermophoresis, we discovered that MgIG directly binds to hydroxysteroid 11-beta dehydrogenase 1 (HSD11B1) at residue 187, a finding corroborated by molecular dynamics simulations. In vivo, MgIG markedly attenuated alcohol-induced liver injury, evidenced by ameliorated histological damage, reduced hepatic steatosis, and normalized liver-to-body weight ratios. In vitro, it effectively reduced lipid accumulation, inflammation, and apoptosis. Mechanistically, RNA sequencing identified isopentenyl diphosphate delta isomerase 1 (IDI1) as a key downstream effector. Hepatocyte-specific genetic manipulations confirmed that MgIG modulates the SREBP2-IDI1 axis, thereby suppressing lipogenesis, inflammatory responses, and apoptotic pathways. We reveal HSD11B1 as a novel direct molecular target of MgIG and elucidate its therapeutic mechanism through the HSD11B1-SREBP2-IDI1 signaling axis, which profoundly impacts ALD pathogenesis. These findings not only validate MgIG’s clinical utility but also highlight a promising new therapeutic target for ALD.

Introduction

Alcohol-associated liver disease (ALD) encompasses a spectrum of hepatic pathologies ranging from steatosis to fibrosis, cirrhosis, and ultimately, hepatocellular carcinoma, contributing significantly to the global burden of disease and premature mortality 1,2. With alcohol use disorder affecting approximately 283 million individuals worldwide (5.1% of the population), alcohol emerges as a leading cause of cirrhosis, conferring a 260-fold increased risk of liver-related death3. Excessive alcohol consumption, the primary etiological factor in ALD, triggers a cascade of pathological events, including oxidative stress, inflammation, and lipid metabolism dysregulation4. Current ALD management primarily focuses on alcohol abstinence and supportive care. While potential therapeutic targets, such as oxidative stress pathways, inflammatory cascades, and the gut-liver axis, have been extensively investigated, the identification of druggable hepatic signaling pathways remains elusive 5,6.

Hydroxysteroid 11-beta dehydrogenase 1 (HSD11B1), a cortisol-regenerating enzyme predominantly expressed in the liver and kidneys, elevates endogenous glucocorticoids and has been implicated in the pathogenesis of metabolic dysfunction-associated steatotic liver disease (MASLD) and liver fibrosis 7,8. Similarly, isopentenyl diphosphate delta isomerase 1 (IDI1), a cytoplasmic enzyme involved in lipid metabolism, has been identified as a key risk factor for hepatocellular carcinoma 9 and intrahepatic cholestasis 10. Emerging evidence suggests that exercise may ameliorate MASLD by downregulating IDI1 expression 11. However, the precise roles of HSD11B1 and IDI1 in ALD progression remain to be elucidated.

Magnesium isoglycyrrhizinate (MgIG), a fourth-generation glycyrrhizin (GL) derivative and a magnesium salt of a single stereoisomer (Fig. 1A), exhibits enhanced pharmacological properties compared to its predecessors. As an 18α-GL, MgIG possesses greater lipophilicity than the β-isomer, facilitating superior binding to target cell receptors and steroid hormones 12. This enhanced binding capacity translates to potent anti-inflammatory effects, hepatoprotective properties, and improved liver function 13. MgIG has demonstrated therapeutic efficacy in various liver diseases, including drug-induced liver injury (DILI) 14, MASLD 15, and liver fibrosis 16. Notably, MgIG has been preliminarily shown to inhibit ethanol-induced activation of the hedgehog signaling pathway in hepatocytes 17 and attenuate acute alcohol-induced hepatic steatosis in a zebrafish model by modulating lipid metabolism-related gene expression 18. Furthermore, MgIG has been recognized by the Chinese Society of Hepatology for its clinical utility in ALD treatment 19. Despite its therapeutic promise and proven safety, the precise molecular targets of MgIG in the liver remain poorly defined, hindering the development of optimized treatment strategies for ALD. This study employed in vivo and in vitro ALD models to investigate the hepatoprotective mechanisms of MgIG, revealing its direct interaction with HSD11B1 as a key mediator of its therapeutic effects and the involvement of downstream signaling of the sterol regulatory element binding protein 2 (SREBP2)-IDI1 axis.

MgIG alleviates liver damage in a mouse model of chronic-binge alcoholic liver disease (the NIAAA model).

(A) Chemical structure of MgIG. (B) Flowchart illustrating the modeling process for the NIAAA model. (C) Representative results of H&E and Oil Red O staining from the livers of mice in Ctrl, A-Ctrl and MgIG groups (n = 5). (D) Alterations in NAS (NAFLD activity score) and Oil Red O quantification (a.v.: arbitrary value) (n = 5). (E) Ratios of liver weight to body weight (LW/BW) in mice (n = 5). (F) Alterations in serum biochemical parameters (ALT, AST and TG) in mice in three groups (n = 5). (G) Alterations in mRNA expression of lipid metabolism genes (Srebp-1c, Srebp2, Acc1, and Scd1), systemic inflammation markers (Tnf-α, Il-6, Il-6, and Il-16), and apoptosis-related genes (Bax and Bcl2) in the mice liver. The data are presented as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001, ****P < 0.0001. Scale bar: 50 μm.

Methods

Chemicals and reagents

MgIG was generously provided by Chia-Tai Tianqing Pharmaceutical Group Co., Ltd. (Nanjing, China) in the form of a magnesium isoglycyrrhizinate injection (5 mg/ml). High-purity ethanol was obtained from MACKLIN (Shanghai, China). Palmitic acid (PA) and fatty acid-free bovine serum albumin (BSA) were purchased from Sigma-Aldrich (St. Louis, MO, USA). All cell culture reagents and consumables were obtained from Gibco (Carlsbad, CA, USA) or Corning Incorporated (Corning, NY, USA). Primary antibodies against tumor necrosis factor-α (TNF-α, #11948), interleukin-6 (IL-6, #12912), glyceraldehyde-3-phosphate dehydrogenase (GAPDH, #2118S), Bax (#2772S), Bcl-2 (#3498S), and hemagglutinin (HA, #3724S) were purchased from Cell Signaling Technology (Shanghai, China). Antibodies against IDI1 (#11166-2-AP) and SREBP2 (#28212-1-AP) were obtained from Proteintech (Wuhan, China). An antibody against HSD11B1 (#AF3397) was purchased from R&D Systems (Minneapolis, MN, USA). A Flag antibody (F1804) was purchased from Sigma-Aldrich. All antibody validation experiments were performed according to the manufacturers’ protocols. Protein A/G Magarose beads (#80105G) were purchased from Invitrogen (Carlsbad, CA, USA).

Animal experiments

Male C57BL/6 wild-type mice (7 weeks old; 19-21 g) were purchased from Guangzhou Qingle Biosciences Co., Ltd. (Guangzhou, China). Mice were acclimated to the housing environment for one week prior to experimental procedures. Alcoholic liver injury was induced using a modified National Institute on Alcohol Abuse and Alcoholism (NIAAA) model 20. Briefly, mice (n = 4 per group) were initially fed ad libitum with the control (Ctrl) Lieber-DeCarli liquid diet for 5 days to facilitate acclimation. Subsequently, the ALD groups (designated as ’A-Ctrl’ and ’MgIG’ in figures) received the Lieber-DeCarli diet containing 5% (v/v) ethanol for 10 days, while the control group (designated as ’Ctrl’ in figures) received an isocaloric control diet. Body weight and food intake were monitored daily. On day 11, ethanol-fed mice and their pair-fed controls were administered a single dose of ethanol (5 g/kg body weight) or an isocaloric maltose dextrin solution, respectively, via oral gavage in the early morning. Mice were euthanized 9 h later (Fig. 1B). A vehicle-MgIG control group was not included in this study because: (1) MgIG is a clinically approved drug with an established safety profile; (2) the dosage used in this study was calculated based on human clinical dosages using a standard conversion formula; and (3) the vehicle safety of MgIG with similar dose has been previously confirmed in an animal study 21. For viral infections, mice (n = 5 per group) received tail vein injections of 5 × 1011 genome copies of either AAV8 control or AAV-shRNA/plasmid. After 14 days, mice were fasted for 4 h at the end of the dark cycle and then euthanized to confirm hepatic upregulation or downregulation of Hsd11b1, Srebp2, or Idi1. These mice were then subjected to the NIAAA model and/or MgIG administration as described above. Target gene expression in the liver was verified using quantitative PCR and Western blotting. All experimental procedures were approved by the Ethical Committee of Jinan University, China (IACUC-20220708-04).

RNA sequencing and functional enrichment analysis

Total RNA was extracted from liver tissue samples using TRIzol reagent (Invitrogen) following the manufacturer’s instructions. RNA quality was assessed using a Nanodrop ONE spectrophotometer (Thermo Fisher, Waltham, MA, USA). Samples with A260/A280 ratios above 1.8 and A260/A230 ratios above 2.0 were deemed acceptable for further processing. RNA integrity was evaluated using an Agilent 2200 TapeStation (Agilent Technologies, Santa Clara, CA, USA), and only samples with an RNA integrity number above 7.0 were used for library preparation. Ribosomal RNA (rRNA) was depleted from total RNA using the Epicentre Ribo-Zero rRNA Removal Kit (Illumina) and fragmented to an average size of 200 bp. First-strand and second-strand cDNA synthesis, followed by adapter ligation and low-cycle enrichment, were performed using the NEBNext Ultra RNA Library Prep Kit for Illumina (New England Biolabs, Ipswich, MA, USA). Library quality was assessed using the Agilent 2200 TapeStation and Qubit 2.0 fluorometer (Thermo Fisher). Libraries were diluted to 10 pmol/L and subjected to cluster generation on a pair-end flow cell, followed by sequencing (2 × 150 bp) on an Illumina HiSeq 3000. Raw sequencing reads were processed to remove adapter sequences, low-quality reads, and reads containing poly-N stretches. Clean reads were aligned to the mouse reference genome using HISAT2 with default parameters. Gene expression levels were quantified using HTSeq, and differential expression analysis was performed using DESeq with read counts as input. The Benjamini-Hochberg method was used to adjust p-values for multiple testing. Differentially expressed genes (DEGs) were defined as those with a fold change > 2 and an adjusted p-value < 0.05. Heatmap visualization and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analysis were performed using the identified DEGs. A p-value < 0.05 was considered statistically significant for KEGG pathway enrichment.

Biochemical and cytokine analyses of mice serum and cell supernatants

Serum levels of alanine aminotransferase (ALT), aspartate aminotransferase (AST), triglyceride (TG) and total cholesterol (TC) were measured using BK2800 (BIOBASE, Jinnan, China). Cell supernatants cytokine levels were determined by using corresponding ELISA kits from R&D Systems (TNF-α: #VAL609; IL-6: #VAL604G).

Liver tissue histology

Liver tissue samples were fixed in 10% neutral buffered formalin and subsequently embedded in paraffin. Tissue sections (5 μm thickness) were prepared and stained with hematoxylin and eosin (H&E) and Oil Red O for histological examination. Images were acquired using a LEICA Qwin Image Analyzer (Leica Microsystems, Milton Keynes, UK). The nonalcoholic fatty liver disease activity score (NAS) was determined for each group as previously described 22.

Cell culture and transfection

The AML-12 mouse normal hepatocyte cell line was obtained from the Cell Bank of Type Culture Collection, Chinese Academy of Sciences (Shanghai, China). Cells were cultured in Dulbecco’s modified Eagle’s medium supplemented with 10% (v/v) fetal bovine serum, incubated at 37 °C with 5% CO2 in a cell incubator. To induce an ALD-like phenotype in AML-12 cells, cells were exposed to a combination of 25 mmol/L ethanol and 0.1-1 mmol/L palmitic acid (PA; Sigma-Aldrich; #P0500) for 24 h to determine the optimal concentration for inducing cellular injury, as previously described (12). We chose the combination of ethanol and palmitic acid in the in vitro experiments because ethanol-only treatment could not phenocopy alcoholic cell death, inflammation, oxidative stress, and the dysregulated lipid metabolism in hepatocytes exhibited in early-stage ALD 23–26. Following this initial treatment, varying concentrations of MgIG were added to the culture medium for an additional 24-hour to assess its effects and determine the optimal dose. For gene knockdown and overexpression experiments, Lipofectamine 3000 reagent (Thermo Fisher; #L3000001) was used to transfect AML-12 cells with Hsd11b1 or Idi1-targeting constructs in 6-well plates.

Cell lipid accumulation, viability, and apoptosis assays

Intracellular lipid droplets were visualized by staining AML-12 cells with Nile Red. Briefly, cells were washed with phosphate-buffered saline (PBS), fixed with 4% formaldehyde for 10 min, and then stained with Nile Red solution (0.1 mg/mL; #N8440, Solarbio, Beijing, China) for 10 min at room temperature in the dark. Cells were then counterstained with DAPI (5 μg/mL; Sigma-Aldrich; D9542) for 5 min. Cell viability and apoptosis were assessed in 96-well plates using a CCK8 cell viability assay and a lactate dehydrogenase (LDH) cytotoxicity assay kit, respectively, according to the manufacturer’s instructions (MedChem Excess, Shanghai, China; HY-K1090 and HY-K0301).

Quantitative PCR

Total RNA was extracted from liver tissue or cultured cells using TRIzol reagent. The first strand cDNA was synthesized from total RNA using a PrimeScript RT Reagent Kit (Takara, Shiga, Japan; #RR047A) following the manufacturer’s instructions. Quantitative PCR reaction was performed with the SYBR Premix Taq Quantitative PCR Kit (Takara) according to the manufacturer’s instructions, on a qTOWER3 machine (Analytik Jena AG, Jena, Germany). Primer information is as listed in Supporting Information Table S1. β-actin was used as an internal control. The relative quantification of mRNA expression levels was calculated using the 2−ΔΔCt method. All qPCR experiments were conducted in compliance with the MIQE guidelines 27.

Protein extraction and Western blot

Samples were lysed using Pierce RIPA buffer (Thermo Fisher) and their protein concentrations were measured with the Bio-Rad Protein Assay (Bio-Rad, Hercules, CA). Western blot analyses of all proteins were conducted with β-actin serving as the internal control.

Coimmunoprecipitation (Co-IP)

Co-IP buffer (50 mM Tris-HCl, 5 mM EDTA, 150 mM NaCl, and 1% NP-40 pH 7.6) mixed with protease inhibitor cocktail (Roche, Bern, Switzerland) were used to lyse the cells. The samples were then incubated with the corresponding antibodies and Protein A/G Magarose beads at 4°C overnight.

Protein structure modeling and molecular docking

We first employed DecoupleR’s 28 built-in Univariate Linear Model (ULM) to compute the transcription factor activity perturbed by MgIG, based on the expression of differentially expressed genes. The findings revealed that Srebf2 was the transcription factor most significantly reduced by MgIG. We then identified potential SREBP2/IDI1-interacting proteins using the STRING and PubMed databases. The 3D structures of these proteins were obtained from the Protein Data Bank (PDB) or UniProt, while the 3D structure of MgIG was retrieved from PubChem. Molecular docking simulations were performed using Schrödinger software to predict the binding affinity (Glide score) of MgIG to each protein. The lowest-energy docking conformations were visualized using PyMOL.

Microscale thermophoresis (MST) assay

The binding interaction between MgIG and HSD11B1 was assessed using a Monolith NT.115 Blue/Green instrument (NanoTemper Technologies, Munich, Germany). Initially, we evaluated the affinity and labeling efficiency of the dye with the His-tagged protein. Subsequently, HSD11B1 proteins (100 nM) were labeled and incubated with MgIG at a concentration gradient ranging from 50 µM to 1.53 nM for 30 min at room temperature. The samples were then analyzed at 60% MST power and a temperature of 25°C. Dissociation constants (Kd) were calculated based on a 1:1 binding stoichiometry.

Molecular dynamics (MD) simulations

Three molecular systems were constructed in this study: first, Compound-HSD11B complex was established through molecular docking. Second, the last frame from 100 ns MD simulation was used to generate APO-HSD11B1 by removing the ligand. Finally, based on this conformation and reported portal vein ethanol concentrations in ALD, five ethanol molecules (0.1 g/dL) were incorporated to construct the EtOH-HSD11B1 system, simulating the ALD environment 29–31. For each system, receptor was prepared and missing atoms of residues were fixed by the advanced PDB-Preparation tool in Yinfo Cloud Computing Platform using PDBFixer and the tLEaP module in AmberTools 20. The AM1-BCC charges were calculated for compound magnesium isoglycyrrhizinate by the Amber antechamber program 32. MD simulations was performed using AmberTools 20 package with AMBER ff19SB 33 and GAFF 34 force field.

The system was solvated by a truncated octahedron water box using OPC water model with a margin of 10 Å. Periodic boundary condition (PBC) was used and the net charge neutralized by Na+ ions. Nonbonded van der Waals interactions were calculated using the Lennard-Jones 12-6 potentials with a 10 Å cutoff, while long-range electrostatics were treated using the Particle Mesh Ewald (PME) algorithm. The SHAKE algorithm was applied to constrain bonds involving hydrogen atoms 35. To removed improper atom contacts, the structure was first minimized by (1) 2500 steps of steepest descent and 2500 steps of conjugate gradient, under a harmonic constraint of 10.0 kcal/(mol·Å2) on heavy atoms; (2) relaxing the entire system by 10000 steps of steepest descent and 10000 steps of conjugate gradient. And then the system was gradually heated up to 300 K by a 20 ps NVT simulation. Subsequently, two steps of equilibration phases were carried out: (1) a 200 ps NPT simulation with constraints on heavy atoms followed by (2) a 1 ns NVT simulation without restraint. The temperature was maintained at 300 K using the Berendsen thermostat with 1 ps coupling constant and the pressure at 1 atm using Monte Carlo barostat with 1 ps relaxation time. Finally, the system was subjected to a 100 ns NVT simulation with a time step of 2 fs. The root-mean-square deviation (RMSD), root-mean-square fluctuation (RMSF), radius of gyration (RG), solvent-accessible surface area (SASA) and hydrogen bonds were analyzed by the CPPTRAJ module, while principal component analysis (PCA) and dynamic cross-correlation matrix (DCCM) were analyzed by R package Bio3D 36. The binding free energies were calculated using the Molecular Mechanics Generalized Born (MM/PBSA) method for the 100 ns MD trajectory 37.

HSD11B1 enzyme activity assays

The enzyme activity of HSD11B1 in cells was evaluated according to its capability to convert cortisone to cortisol 38. AML-12 cells were seeded into 6-well culture plates and induced ALD as above. Different concentrations of MgIG (0.1, 0.25, and 0.5 mg/mL) were added 24 h prior to the co-treatment, with a control group included. AML-12 cells were exposed to 160 nmol/L cortisone for 24 h. The reaction mixtures were collected and analyzed for cortisol levels using an ELISA kit (R&D Systems, Minneapolis, MN, USA), according to the manufacturer’s instructions.

Statistical analysis

The data from each group are presented as the mean ± standard deviation (SD). For data that followed a normal distribution, statistical comparisons between two groups were conducted using an unpaired two-tailed Student’s t-test; for comparisons involving three or more groups, a two-way ANOVA followed by a Student-Newman-Keuls post hoc test was applied (Prism 5.0, Graphpad Software, Inc., San Diego, CA). A P-value of less than 0.05 was deemed statistically significant.

Results

MgIG alleviates liver injury in a mouse model of ALD

To investigate the hepatoprotective effects of MgIG in vivo, we employed a well-established chronic-binge NIAAA mouse model of ALD (Fig. 1B). Based on the drug’s clinical instructions, previous studies 21,39, and our preliminary experimental results (Fig. S1), we determined an optimal MgIG dose of 50 mg/kg. Compared to mice fed a normal diet (Ctrl group), mice in the alcohol-fed control group (A-Ctrl) exhibited characteristic histological features of ALD, including steatosis and inflammatory cell infiltration, resulting in an elevated NAS. MgIG treatment effectively attenuated these pathological changes (Fig. 1C and 1D). Consistent with these histological findings, the liver-to-body weight ratio, a marker of liver injury, was significantly increased in the A-Ctrl group, and this increase was markedly reduced by MgIG treatment (Fig. 1E). Notably, serum levels of liver enzymes (ALT and AST) and triglycerides (TG), indicators of liver function and lipid metabolism, were significantly different between the A-Ctrl and MgIG-treated groups (Fig. 1F). In line with the observed histological and physiological improvements, MgIG treatment also modulated the expression of genes involved in lipid metabolism (Srebp-1c, Srebp2, Acc1, and Scd1), inflammation (Tnf-α and Il-6), and apoptosis (Bax and Bcl2) in the liver tissue of A-Ctrl mice (Fig. 1G).

MgIG protects against ethanol-induced hepatocyte injury via IDI1

To further elucidate the molecular mechanisms underlying the hepatoprotective effects of MgIG, we performed RNA sequencing analysis on liver tissue from the NIAAA mouse model. DEG analysis revealed a significant upregulation of Idi1 in the A-Ctrl group compared to the Ctrl group (Fig. 2A). Furthermore, KEGG pathway enrichment analysis identified metabolic pathways among the top five downregulated pathways in the MgIG-treated group compared to the A-Ctrl group, with Idi1 consistently ranked among the top two genes in these pathways (Fig. 2C). To further investigate the role of IDI1 and its potential interaction with MgIG, we established an in vitro model of ethanol/palmitic acid (EtOH/PA)-induced hepatocyte injury using AML-12 cells. We first optimized the EtOH/PA concentrations to induce significant cell death and lipid accumulation (Fig. S2), identifying 250 mmol/L ethanol and 0.2 mmol/L PA as the optimal combination. MgIG treatment (0.1-1.0 mg/mL) demonstrated a dose-dependent protective effect against EtOH/PA-induced injury, as evidenced by improved cell viability, reduced lipid accumulation, and decreased apoptosis (Fig. 2D and 2E). Consistent with the in vivo findings, EtOH/PA treatment increased the expression of genes involved in lipid metabolism (Acc1 and Scd1) and inflammation (Tnf-α and Il-6), and MgIG treatment effectively reversed these effects (Fig. 2F). Based on these results, we selected 0.25 mg/mL as the optimal MgIG concentration for subsequent in vitro experiments.

MgIG protects ethanol-induced hepatocyte injury in a cell model.

(A) Volcano plot analysis showing differentially expressed genes between the MgIG group (ALD+MgIG) and the A-Ctrl (ALD only) group after RNA-seq in liver of mice. (B) The top 5 regulated pathways (both up- and down-regulated) and the top 3 genes within each pathway are shown. (C) Volcano plot analysis showing differentially expressed genes between the A-Ctrl group and the Ctrl group after RNA-seq in liver of mice. (D) Changes in AML-12 cell viability, apoptosis, and Nile Red staining signals after ethanol/PA treatment, with or without co-treatment with different MgIG doses (0, 0.1, 0.25, 0.5, and 1 mg/ml) (n = 4). (E) Representative images of Nile Red staining in AML-12 cells treated with ethanol/PA, with or without co-treatment with different MgIG doses. (F) Changes in mRNA expression of lipid metabolism genes (Acc1 and Scd1) and systemic inflammation markers (Tnf-α and Il-6) in AML-12 cells treated with ethanol/PA, with or without co-treatment with different MgIG doses. Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001. Scale bar: 20 μm.

In line with the in vivo observations, Idi1 expression was significantly increased in AML-12 cells following EtOH/PA treatment, and this effect was attenuated by MgIG treatment (Fig. 3A and S3A-B). As shown in Fig. 3B and 3C, transfection with siRNA and plasmid effectively decreased or increased Idi1 mRNA levels without affecting cell viability, respectively. Knockdown of Idi1 significantly ameliorated EtOH/PA-induced cell injury, reducing apoptosis, inflammatory cytokine levels, and lipid accumulation, while Idi1 overexpression exacerbated these effects (Fig. 3D-3G). Taken together, these findings suggest that MgIG protects against ethanol-induced hepatocyte injury, at least in part, through the modulation of IDI1.

IDI1 is involved in MgIG-mediated hepatocyte protection against ethanol.

(A) Quantitative PCR validation of RNA-seq results revealed changes in Idi1 gene expression in AML-12 cells treated with ethanol/PA, with or without 0.25 mg/ml MgIG co-treatment (n = 4). (B) Quantitative PCR results confirmed the knockdown efficiency of Idi1 genes by siRNA in AML-12 cells. The changes in AML-12 cell viability following Idi1 siRNA transfection (24 h) were also assessed (n = 4). (C) Quantitative PCR results confirmed the overexpression efficiency of Idi1 genes via plasmid transfection in AML-12 cells. Changes in AML-12 cell viability following Idi1 plasmid transfection (24 h) were also evaluated (n = 4). (D) Changes in cell viability and apoptosis ratios were assessed in ethanol/PA-treated AML-12 cells, with or without 0.25 mg/ml MgIG, following Idi1 knockdown/overexpression (n = 4). (E, F) Western blot results for TNF-α, IL-6, Bax, and Bcl-2 and cell supernatant results for TNF-α and IL-6 in AML-12 cells treated with ethanol/PA and ethanol/PA + MgIG, with or without Idi1 knockdown/overexpression (n = 3). (G, H) Nile Red staining area (%) with corresponding representative cell staining images. Data are expressed as mean ± SD. For Western blot quantification: *P < 0.05, **P < 0.01, ***P < 0.001. Scale bar: 20 μm.

MgIG directly binds to HSD11B1

To identify potential direct binding partners of MgIG, we initially performed molecular docking simulations between MgIG and IDI1. However, the resulting Glide score of -2.74 indicated a lack of favorable binding interactions, which implied that there should be an immediate binding protein in the upstream of IDI1. To identify potential upstream regulators of Idi1 expression, we utilized the ULM within the DecoupleR package to analyze transcription factor activity. This analysis identified SREBP2 as the most significantly affected transcription factor (Fig. 4A). We then expanded our search to include upstream regulators of IDI1 identified using the STRING database. Among these proteins, HSD11B1 exhibited the highest binding affinity for MgIG, with a Glide score of -8.75 (Fig. 4B). Given the homology between human and mouse Hsd11b1 and the need for future translational research, we focused on validating the interaction between human HSD11B1 and MgIG. We conducted 100 ns MD simulations for Compound-HSD11B1 (MgIG-HSD11B1 binding in physiological condition) and EtOH-HSD11B1 (MgIG-HSD11B1 binding in alcoholic condition), with free HSD11B1 as a control. The results revealed that HSD11B1 exhibited high flexibility and dynamic motion in its unbound state but became significantly more rigid and stable upon binding to MgIG, particularly at residues 219–233 (Fig. 4C-4E). This structural stabilization was further supported by the radius of gyration curves, which indicated a more compact conformation upon binding (Fig. S4A and SB). Further analyses, including PCA and DCCM, demonstrated alterations in motion direction, dynamic patterns, and residue correlations. Specifically, upon binding, HSD11B1 exhibited reduced motion amplitude and weaker residue correlations, with its dynamic patterns becoming more disordered (Fig. S4C-4E). In the Compound-HSD11B1 system (Fig. 4E), key interactions included hydrogen bonds (Tyr177, Tyr183), a salt bridge (Lys187) and hydrophobic interactions (Leu126, Leu217, Ala223, Ala226, and Ile230). In contrast, the EtOH-HSD11B1 system (Fig. 4F) exhibited hydrogen bonds (Thr124, Ser170, Tyr183, Leu217, and Arg269) along with an additional salt bridge (Tyr183 and Arg269). Notably, the EtOH-HSD11B1 system demonstrated stronger hydrogen bonding and more favorable binding free energy compared to the Compound-HSD11B1 system (Fig. 4G and S4F), suggesting enhanced stability and binding affinity in an ethanol environment. Based on molecular docking and MD results, we further validated the binding between MgIG and the human full-length wild-type (WT) HSD11B1 protein as well as its site-directed mutants (Tyr177, M1; Tyr183, M2; Lys187, M3) using MST. The Kd value of the WT protein was 6.35 μM (Fig. 4H), while those of M1, M2, and M3 were 48.6 μM, 11.5 μM, and 135.6 μM, respectively (Fig. 4I). These data indicate that MgIG primarily exerts its anti-ALD effect by inhibiting HSD11B1 through the critical Lys187 site.

HSD11B1 is the direct binding protein of MgIG for the protection of ethanol-induced hepatocytes injury.

(A) Bar chart displaying the top 10 upregulated and downregulated transcription factor activity scores in the MgIG (ALD+MgIG) group compared to the A-Ctrl (ALD only) group. (B) The glide score of MgIG binding to the protein structure as determined by molecular docking analysis. (C, D) RMSD and RMSF analysis of the three systems: APO-HSD11B1 (blue) represents unbound HSD11B1 in a physiological saline system, Compound-HSD11B1 (red) represents HSD11B1 bound to MgIG in a physiological saline system, and EtOH-HSD11B1 (green) represents HSD11B1 bound to MgIG in a 0.1 mg/mL ethanol solvent system. (E, F) Molecular modeling analysis of MgIG binding at the HSD11B1 domain in normal saline and ethanol systems. Left: Cartoon view of MgIG at the HSD11B1 binding site. Right: Close-up surface view of MgIG at the HSD11B1 binding sites. (G) Hydrogen bond analysis of HSD11B1-MgIG interactions in normal saline and ethanol systems. (H, I) The microscale thermophoresis (MST) assay demonstrated direct binding between varying doses of MgIG and human HSD11B1 protein at residues 187. WT: wild-type HSD11B1; M1, M2, M3: point mutations at Tyr177, Tyr183, and Lys187, respectively.

To further investigate the functional significance of this interaction, we modulated Hsd11b1 expression in AML-12 cells using siRNA- and plasmid-mediated knockdown and overexpression, respectively. As shown in Fig. 4A-4C, transfection with siRNA and plasmid effectively decreased or increased Hsd11b1 mRNA levels without affecting cell viability, respectively. Knockdown of Hsd11b1 significantly attenuated EtOH/PA-induced inflammation, apoptosis, and lipid accumulation, even in the absence of MgIG treatment. Conversely, overexpression of Hsd11b1 exacerbated these effects. Importantly, MgIG treatment partially reversed the detrimental effects of Hsd11b1 overexpression (Fig. 5D-5F). To further investigate whether the binding of MgIG to HSD11B1 affects its enzymatic activity, we added different concentrations of MgIG (0.1, 0.25, and 0.5 mg/mL) to the cellular model. ELISA results showed that HSD11B1 activity was significantly elevated in the ALD group, whereas increasing concentrations of MgIG led to a dose-dependent reduction in HSD11B1 activity (Fig. 5G). Considering the quite low basal expression of Hsd11b1 in normal AML-12 cells, we further examined cortisol levels in the supernatant of AML-12 cells overexpressing Hsd11b1, with or without MgIG co-treatment (Fig. 5H). These findings suggested that MgIG exerted its protective effects against EtOH/PA-induced hepatocyte injury, at least in part, by directly binding to and modulating the activity of HSD11B1.

HSD11B1 is involved in MgIG-mediated hepatocyte protection against ethanol.

(A) Quantitative PCR validation of RNA-seq results revealed changes in Hsd11b1 gene expression in AML-12 cells treated with ethanol/PA, with or without 0.25 mg/ml MgIG co-treatment (n = 4). (B, C) Quantitative PCR confirmed the knockdown efficiency of Hsd11b1 (siRNA) and the overexpression efficiency of Idi1 (plasmid) in AML-12 cells, and cell viability changes were assessed 48 h after transfection (n = 4). (D) Nile Red staining area (%) with corresponding representative cell staining images (n=4). (E, F) Western blot results for TNF-α, IL-6, Bax, and Bcl-2 and cell supernatant results for TNF-α and IL-6 in AML-12 cells treated with ethanol/PA and ethanol/PA + MgIG, with or without Hsd11b1 knockdown/overexpression (n = 3). Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001. Scale bar: 20 μm.

MgIG protects hepatocyte partially through the HSD11B1–SREBP2–IDI1 axis

To investigate the relationship between SREBP2 and HSD11B1, we conducted co-IP experiments, which revealed a direct interaction between the precursor form of SREBP2 (p-SREBP2) and HSD11B1. This interaction was weakened following MgIG treatment (Fig. 6A and 6B). To further explore this interaction, we modulated Hsd11b1 expression in EtOH/PA induced AML-12 cells with or without MgIG treatment (Fig. 6C and 6D). Knockdown of Hsd11b1 resulted in an accumulation of p-SREBP2, while Hsd11b1 overexpression increased the levels of nuclear SREBP2 (n-SREBP2), an effect further enhanced by the EtOH/PA treatment. These findings suggest that HSD11B1 may regulate the processing and nuclear translocation of SREBP2. Immunofluorescent analysis confirmed these observations (Fig. 6E). As shown in Fig. 6F, the co-IP results indicated that HSD11B1 also interacted with its downstream protein IDI1. In addition, the dual-luciferase reporter assay demonstrated that Srebp2 positively regulates Idi1 expression (Fig. 6G). In in vivo experiments, it was confirmed that in normal liver tissue, the expression of Srebp2 and Idi1 followed a similar trend in response to overexpression or knockdown of Hsd11b1 (Fig. 6H and 6I). Knockdown of Srebp2 resulted in a decrease in Idi1 expression, without affecting Hsd11b1 levels. Conversely, neither knockdown nor overexpression of Idi1 influenced the expression of the upstream genes Hsd11b1 or Srebp2. In liver tissue from ALD, the expression changes of upstream and downstream genes upon overexpression or knockdown of Hsd11b1 or Idi1 mirrored those seen in normal liver tissue. However, Srebp2 knockdown induced a negative feedback effect, reducing Hsd11b1 expression, which was not observed in normal liver tissue (Fig. 6J and 6K).

MgIG exerts its protective effect via the HSD11B1-SREBP2-IDI1 axis in ALD model.

(A, B) Co-IP was used to verify the direct binding between HSD11B1 and SREBP2 with or without MgIG treatment. (C, D) Alterations in protein levels of HSD11B1, p-SREBP2, n-SREBP2, and IDI1 in AML-12 cells induced by EtOH/PA, following knockdown or overexpression of Hsd11b1, with and without MgIG treatment (n = 3). (E) Immunofluorescent staining was conducted to visualize the distribution and expression of SREBP2 (red) in EtoH/PA-induced AML-12 cells, with or without MgIG, following Hsd11b1 knockdown or overexpression. (F) Co-IP was used to verify the direct binding between HSD11B1 and IDI1. (G) Effects of Srebp2 on Idi1 transcriptional regulation were measured by luciferase assays in AML-12 and 293T cell lines. Idi1-wild-type (WT) or Idi1-mutant (Mut), plasmids with WT promoter cDNA clone of Idi1 or with mutant promoter cDNA clone plasmid; pRL-TK, an internal control reporter plasmid. (H, I) The expression levels of Hsd11b1, Srebp2, and Idi1 in normal liver were measured following the knockdown of Hsd11b1, Srebp2, and Idi1, or the overexpression of Hsd11b1 and Idi1, respectively (n = 4). (J, K) The expression levels of Hsd11b1, Srebp2, and Idi1 in ALD liver were measured following the knockdown of Hsd11b1, Srebp2, and Idi1, or the overexpression of Hsd11b1 and Idi1, respectively (n = 5). Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001. ****P < 0.0001. Scale bar: 10 μm.

To further investigate the roles of HSD11B1, SREBP2, and IDI1 in the in vivo ALD model, we used AAV8-mediated shRNA delivery to knock down their expression or employed overexpression plasmids to increase their expression specifically in hepatocytes. As shown in Fig. S6A-6C, knockdown or overexpression of Hsd11b1 or Idi1 in mice fed a normal control diet did not result in significant changes in liver histology, lipid accumulation, or serum ALT and AST levels. However, in the ALD model, knockdown of Hsd11b1, Srebp2, or Idi1 attenuated ethanol-induced liver injury, as evidenced by improved histological NAS scores, reduced steatosis, and decreased inflammation. MgIG treatment further enhanced these beneficial effects. Conversely, overexpression of Hsd11b1 or Idi1 abolished the therapeutic effects of MgIG on ethanol-induced liver injury (Fig. 7A-7F and S7). Interestingly, modulation of Idi1 expression did not affect the expression of Hsd11b1 or Srebp2, suggesting that IDI1 acts downstream of HSD11B1 and SREBP2. In contrast, modulation of Hsd11b1 expression altered the levels of n-SREBP2 and IDI1 (Fig. S7E-G), confirming that HSD11B1 regulates the SREBP2-IDI1 pathway. Collectively, these data indicate that MgIG protects against ALD, at least in part, by modulating the HSD11B1-SREBP2-IDI1 axis.

MgIG alleviates ALD-induced liver injury via the HSD11B1-SREBP2-IDI1 axis.

(A-D) Representative liver H&E and Oil Red O staining results from ALD mice with Hsd11b1, Srebp2, or Idi1 knockdown or overexpression, with and/or without MgIG co-treatment. Changes in quantitative NAS (NAFLD activity score) and Oil Red staining (area %) were calculated and analyzed (n = 5). (E-F) Changes of serum ALT and TNF-α from ALD mice with Hsd11b1, Srebp2, or Idi1 knockdown or overexpression, with and/or without MgIG co-treatment (n = 5). (G) Alterations in protein levels of HSD11B1, p-SREBP2, n-SREBP 2, and Idi1 in ALD mice, following knockdown or overexpression of Hsd11b1, with and without MgIG co-treatment (n = 3). Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001, ****P < 0.0001. Scale bar: 50 μm.

Discussion

While previous research using a zebrafish model demonstrated that MgIG alleviates alcohol-induced liver injury by modulating lipid metabolism-related gene expression 18, the precise molecular mechanisms and direct targets of MgIG remained unclear. This lack of mechanistic understanding hindered the development of optimized therapeutic strategies for ALD. In this study, we provide compelling evidence that MgIG effectively ameliorates key features of ALD, including hepatic steatosis, inflammation, and apoptosis, in both in vivo and in vitro models. Our findings shed light on the complex interplay of molecular pathways involved in ALD pathogenesis and highlight the therapeutic potential of targeting the HSD11B1-SREBP2-IDI1 axis.

Our RNA sequencing analysis identified IDI1 as a key player in ALD pathogenesis and a critical mediator of MgIG’s hepatoprotective effects. IDI1, an enzyme in the mevalonate pathway, is involved in the biosynthesis of isoprenoids, which are essential for various cellular processes, including cholesterol synthesis. Dysregulation of cholesterol metabolism is a hallmark of ALD, contributing to the accumulation of lipids in the liver. Our findings demonstrate that Idi1 expression is significantly upregulated in the livers of mice subjected to the NIAAA model of ALD, suggesting that increased IDI1 activity may contribute to the development of hepatic steatosis. Genetic manipulation of Idi1 expression further confirmed its role in ALD. Specifically, Idi1 knockdown protected against alcohol-induced liver injury, an effect further enhanced by MgIG treatment. This suggests that reducing IDI1 activity can ameliorate the detrimental effects of alcohol on the liver and that MgIG may exert its therapeutic benefits, at least in part, by suppressing IDI1. Conversely, Idi1 overexpression abolished the therapeutic benefits of MgIG, both in vivo and in vitro, highlighting the importance of IDI1 in mediating MgIG’s effects. These findings are consistent with recent reports highlighting the role of IDI1 in hepatic cholesterol accumulation and lipid toxicity 40 41 and its involvement in hepatocellular carcinoma progression via inhibition of the cGAS-STING pathway 9. Furthermore, our study identified SREBP2, a master regulator of lipid metabolism, as an upstream regulator of IDI1. SREBP2 belongs to a family of transcription factors that control the expression of genes involved in cholesterol and fatty acid biosynthesis. SREBP2 has been implicated in various aspects of liver pathology, including NLRP3 inflammasome activation 42, lipid accumulation 43, liver cancer progression 44, with its target protein IDI1 upregulated in parallel 30. Our findings demonstrate that both SREBP2 and IDI1 are upregulated in response to EtOH/PA treatment and that MgIG effectively inhibits their expression, consistent with the notion that SREBP2 contributes to the development of MASLD 45. The identification of SREBP2 as a key regulator of IDI1 in the context of ALD provides a mechanistic link between lipid metabolism and the pathogenesis of this disease.

To identify the direct molecular target of MgIG, we employed a combination of molecular docking, MD, MST analysis, and genetical manipulation studies. These approaches converged on HSD11B1, a key enzyme in glucocorticoid metabolism, as a high-affinity binding partner of MgIG. HSD11B1 catalyzes the conversion of inactive cortisone to active cortisol in the liver, thereby increasing intracellular glucocorticoid levels. Glucocorticoids are steroid hormones that play a critical role in regulating glucose and lipid metabolism, and their dysregulation has been implicated in the development of metabolic disorders, including type 2 diabetes 46. As a potential inhibitor of HSD11B1 47, GL can improve patients’ insulin and lipid levels 48. In addition, the increased expression of Hsd11b1 enhances the enzymatic reducing activity, promoting a fat-forming phenotype in cell models through elevated cortisol levels 49,50. Meanwhile, Hsd11b1 deficiency prevents hepatic steatosis in high-fat diets-fed mice 51. Our findings demonstrate that MgIG directly binds to the Lys187 of HSD11B1 and that modulation of Hsd11b1 expression in hepatocytes significantly influences the development of ALD.

While some studies have suggested a potential pro-fibrotic role for HSD11B1 inhibition 8, our findings, along with those of other recent studies 7,51,52, support a protective role for Hsd11b1 knockdown in the context of alcoholic liver injury. These discrepancies may be attributed to differences in experimental models and the specific cell types targeted. For instance, the study by Zou et al 8 examined the effects of global Hsd11b1 deficiency, which could trigger compensatory activation of the hypothalamic-pituitary-adrenal axis or paracrine regulatory mechanisms, potentially affecting the pro-fibrotic response. In contrast, our study focused on hepatocyte-specific Hsd11b1 knockdown, which may avoid these confounding factors. Importantly, our study provides evidence for a novel HSD11B1-SREBP2-IDI1 axis in the pathogenesis of ALD. We demonstrate that HSD11B1 regulates the processing and nuclear translocation of SREBP2, which in turn controls the expression of IDI1. Notably, this is consistent with previous studies showing that increased SREBP2 expression and nuclear translocation activate the NLRP3 inflammasome and the mevalonate pathway, thereby promoting inflammation and tumor progression 53,54. This regulatory axis appears to be a key target of MgIG’s therapeutic effects. By directly binding to HSD11B1, MgIG may inhibit its activity, leading to reduced SREBP2 activation and subsequent downregulation of IDI1. This, in turn, could contribute to the observed improvements in hepatic steatosis, inflammation, and apoptosis 55–57.

This study provides mechanistic evidence that MgIG directly targets HSD11B1 and modulates the HSD11B1–SREBP2–IDI1 axis to attenuate ALD. However, several limitations should be acknowledged. First, our findings are derived from preclinical mouse models and hepatocyte systems, and pharmacokinetics, biodistribution, and long-term safety of MgIG remain to be comprehensively evaluated in larger and more diverse populations. Second, although molecular docking and thermophoresis confirmed direct binding of MgIG to HSD11B1, high-resolution structural studies such as X-ray crystallography or cryo-electron microscopy are needed to delineate the precise binding interface and conformational changes. Third, other signaling pathways potentially influenced by MgIG have not been systematically explored and may contribute to its therapeutic effects. Future work should focus on validating these findings in human tissues, optimizing MgIG dosing strategies, and conducting multicenter clinical trials to assess its translational potential and establish HSD11B1 as a druggable target for precision therapy in ALD.

eLife Assessment

This important study reports characterisation of hepatocyte molecular pathways affected by a glycyrrhizin derivative in both in vivo and in vitro mouse models of alcohol-associated liver disease. The authors show convincing evidence indicating that IPP delta isomerase 1 (Idi1) is an intermediate in these pharmacological effects, via the binding of the glycyrrhizin derivative to an upstream regulator of Idi1, HSD11B1, although some more quantitative analyses and better organisation of data would strengthen the study. The findings would be of interest to immunologists and pharmacologists interested in liver inflammation and its amelioration.

Reviewer #1 (Public review):

Summary:

In this article by Xiao et al., the authors aimed to identify the precise targets by which magnesium isoglycyrrhizinate (MgIG) functions to improve liver injury in response to ethanol treatment. The authors found through a series of in vivo and molecular approaches that MgIG treatment attenuates alcohol-induced liver injury through a potential SREBP2-IdI1 axis. This manuscript adds to a previous set of literature showing MgIG improves liver function across a variety of etiologies, and also provides mechanistic insight into its mechanism of action.

Strengths:

(1) The authors use a combination of approaches from both in-vivo mouse models to in-vitro approaches with AML12 hepatocytes to support the notion that MgIG does improve liver function in response to ethanol treatment.

(2) The authors use both knockdown and overexpression approaches, in vivo and in vitro, to support most of the claims provided.

(3) Identification of HSD11B1 as the protein target of MgIG, as well as confirmation of direct protein-protein interactions between HSD11B1/SREBP2/IDI1, is novel.

Weaknesses:

Major weaknesses can be classified into 3 groups:

(1) The results do not support some claims made.

(2) Qualitative analyses of some of the lipid measures, as opposed to more quantitative analyses.

(3) There are no appropriate readouts of Srebp2 translocation and/or activity.

More specific comments:

(1) A few of the claims made are not supported by the references provided. For instance, line 76 states MgIG has hepatoprotective properties and improved liver function, but the reference provided is in the context of myocardial fibrosis.

(2) MgIG is clinically used for the treatment of liver inflammatory disease in China and Japan. In the first line of the abstract, the authors noted that MgIG is clinically approved for ALD. In which countries is MgIG approved for clinical utility in this space?

(3) Serum TGs are not an indicator of liver function. Alterations in serum TGs can occur despite changes in liver function.

(4) There are discrepancies in the results section and the figure legends. For example, line 302 states Idil is upregulated in alcohol fed mice relative to the control group. The figure legend states that the comparison for Figure 2A is that of ALD+MgIG and ALD only.

(5) Oil Red O staining provided does not appear to be consistent with the quantification in Figure 1D. ORO is nonspecific and can be highly subjective. The representative image in Figure 1C appears to have a much greater than 30% ORO (+) area.

(6) The connection between Idil expression in response to EtOH/PA treatment in AML12 cells with viability and apoptosis isn't entirely clear. MgIG treatment completely reduces Idi1 expression in response to EtOH/PA, but only moderate changes, at best, are observed in viability and apoptosis. This suggests the primary mechanism related to MgIG treatment may not be via Idi1.

(7) The nile red stained images also do not appear representative with its quantification. Several claims about more or less lipid accumulation across these studies are not supported by clear differences in nile red.

(8) The authors make a comment that Hsd11b1 expression is quite low in AML12 cells. So why did the authors choose to knockdown Hsd11b1 in this model?

(9) Line 380 - the claim that MGIG weakens the interaction between HSD11b1 and SREBP2 cannot be made solely based on one Western blot.

(10) It's not clear what the numbers represent on top of the Western blots. Are these averages over the course of three independent experiments?

(11) The claim in line 382 that knockdown of Hsd11b1 resulted in accumulation of pSREBP2 is not supported by the data provided in Figure 6D.

(12) None of the images provided in Figure 6E support the claims stated in the results. Activation of SREBP2 leads to nuclear translocation and subsequent induction of genes involved in cholesterol biosynthesis and uptake. Manipulation of Hsd11b1 via OE or KD does not show any nuclear localization with DAPI.

(13) The entire manuscript is focused on this axis of MgIG-Hsd11b1-Srebp2, but no Srebp2 transcriptional targets are ever measured.

(14) Acc1 and Scd1 are Srebp1 targets, not Srebp2.

(15) A major weakness of this manuscript is the lack of studies providing quantitative assessments of Srebp2 activation and true liver lipid measurements.

Reviewer #2 (Public review):

Summary:

In this manuscript, the authors investigated magnesium isoglycyrrhizinate (MgIG)'s hepatoprotective actions in chronic-binge alcohol-associated liver disease (ALD) mouse models and ethanol/palmitic acid-challenged AML-12 hepatocytes. They found that MgIG markedly attenuated alcohol-induced liver injury, evidenced by ameliorated histological damage, reduced hepatic steatosis, and normalized liver-to-body weight ratios. RNA sequencing identified isopentenyl diphosphate delta isomerase 1 (IDI1) as a key downstream effector. Hepatocyte-specific genetic manipulations confirmed that MgIG modulates the SREBP2-IDI1 axis. The mechanistic studies suggested that MgIG could directly target HSD11B1 and modulate the HSD11B1-SREBP2-IDI1 axis to attenuate ALD. This manuscript is of interest to the research field of ALD.

Strengths:

The authors have performed both in vivo and in vitro studies to demonstrate the action of magnesium isoglycyrrhizinate on hepatocytes and an animal model of alcohol-associated liver disease.

Weaknesses:

The data were not well-organised, and the paper needs proofreading again, with a focus on the use of scientific language throughout.

Here are several comments:

(1) In Supplemental Figure 1A, all the treatment arms (A-control, MgIG-25 mg/kg, MgIG-50 mg/kg) showed body weight loss compared to the untreated controls. However, Figure 1E showed body weight gain in the treatment arms (A-control and MgIG-25 mg/kg), why? In Supplemental Figure 1A, the mice with MgIG (25 mg/kg) showed the lowest body weight, compared to either A-control or MgIG (50 mg/kg) treatment. Can the authors explain why MgIG (25 mg/kg) causes bodyweight loss more than MgIG (50 mg/kg)? What about the other parameters (ALT, ALS, NAS, etc.) for the mice with MgIG (50 mg/kg)?

(2) IL-6 is a key pro-inflammatory cytokine significantly involved in ALD, acting as a marker of ALD severity. Can the authors explain why MgIG 1.0 mg/ml shows higher IL-6 gene expression than MgIG (0.1-0.5 mg/ml)? Same question for the mRNA levels of lipid metabolic enzymes Acc1 and Scd1.

(3) For the qPCR results of Hsd11b1 knockdown (siRNA) and Hsd11b1 overexpression (plasmid) in AML-12 cells (Figure 5B), what is the description for the gene expression level (Y axis)? Fold changes versus GAPDH? Hsd11b1 overexpression showed non-efficiency (20-23, units on Y axis), even lower than the Hsd11b1 knockdown (above 50, units on Y axis). The authors need to explain this. For the plasmid-based Hsd11b1 overexpression, why does the scramble control inhibit Hsd11b1 gene expression (less than 2, units on the Y axis)? Again, this needs to be explained.

Author response:

The following is the authors’ response to the original reviews.

Public Reviews:

Reviewer #1 (Public review):

(1) A few of the claims made are not supported by the references provided. For instance, line 76 states MgIG has hepatoprotective properties and improved liver function, but the reference provided is in the context of myocardial fibrosis.

Thank you for the correction. We have made the revision on page 4, line74.

(2) MgIG is clinically used for the treatment of liver inflammatory disease in China and Japan. In the first line of the abstract, the authors noted that MgIG is clinically approved for ALD. In which countries is MgIG approved for clinical utility in this space?

Thank you for this important comment. MgIG has been recommended for the treatment of alcoholic liver disease (ALD) in Chinese clinical guidelines (2018). We have clarified this point in the manuscript (Page 5, Line 79-80).

(3) Serum TGs are not an indicator of liver function. Alterations in serum TGs can occur despite changes in liver function.

Thank you for this important comment. We fully agree that serum triglycerides (TGs) are not a direct indicator of liver function. ALT and AST are more appropriate markers for hepatocellular injury, whereas TG and TC primarily reflect systemic and hepatic lipid metabolism status. We have made the necessary revisions as suggested on page 12, lines 285-288

(4) There are discrepancies in the results section and the figure legends. For example, line 302 states Idil is upregulated in alcohol fed mice relative to the control group. The figure legend states that the comparison for Figure 2A is that of ALD+MgIG and ALD only.

We thank the reviewer for the valuable suggestion. Accordingly, we have revised the legend for Figures 2A and 2B as suggested.

(5) Oil Red O staining provided does not appear to be consistent with the quantification in Figure 1D. ORO is nonspecific and can be highly subjective. The representative image in Figure 1C appears to have a much greater than 30% ORO (+) area.

Thank you for this insightful comment. We acknowledge that Oil Red O (ORO) staining can be influenced by background signal and may appear subjective in representative images. In our quantification, only well-defined lipid droplets with strong positive staining were included, while diffuse background staining (e.g., light reddish hue) was excluded. This may explain the apparent discrepancy between the representative image and the quantified ORO-positive area. To further strengthen the reliability of our findings, we additionally measured hepatic triglyceride (TG) and total cholesterol (TC) levels. These biochemical assays yielded results consistent with the ORO quantification, thereby supporting our conclusion regarding lipid accumulation. Please refer to page12, lines 285-288. As requested, we have added the required information to Figures 1G.

(6) The connection between Idil expression in response to EtOH/PA treatment in AML12 cells with viability and apoptosis isn't entirely clear. MgIG treatment completely reduces Idi1 expression in response to EtOH/PA, but only moderate changes, at best, are observed in viability and apoptosis. This suggests the primary mechanism related to MgIG treatment may not be via Idi1.

Thank you very much. We agree that although MgIG almost completely reverses Idi1 expression induced by EtOH/PA, the improvements in cell viability and apoptosis are only moderate, suggesting a potential discrepancy between these observations. This may indicate that Idi1 functions as a permissive factor, rather than the sole mediator, in this pathological process. In other words, while modulation of Idi1 contributes to the protective effects of MgIG, additional pathways are likely involved in mediating its overall impact on hepatocyte viability and apoptosis. We have clarified this point in the revised manuscript (Page 12, Lines 325–335), stating that MgIG exerts its protective effects against ethanol-induced hepatocellular injury, at least in part, through the regulation of Idi1.

(7) The nile red stained images also do not appear representative with its quantification. Several claims about more or less lipid accumulation across these studies are not supported by clear differences in nile red.

Thanks a lot. We acknowledge that Nile Red staining can be influenced by imaging conditions and may appear less distinct in representative images, which could affect visual interpretation. To minimize subjectivity, all images were analyzed using a consistent and standardized thresholding method across groups. We agree that the visual differences in Nile Red staining alone may not be sufficiently pronounced to fully support the quantitative conclusions. Therefore, to strengthen the reliability of our findings, we have included additional biochemical measurements, including serum TG and TC levels, as well as hepatic TG and TC content. These independent assays consistently support the observed changes in lipid accumulation. The corresponding data have been added to the revised manuscript (page 12, lines 285-288)

(8) The authors make a comment that Hsd11b1 expression is quite low in AML12 cells. So why did the authors choose to knockdown Hsd11b1 in this model?

Thank you for this important comment. Although the basal expression of Hsd11b1 in untreated AML-12 cells is relatively low, we observed that it is inducible upon EtOH/PA stimulation, indicating its functional relevance under stress conditions. Therefore, knockdown experiments were performed to assess its contribution to EtOH/PA-induced hepatocellular injury. We have clarified this point in the revised manuscript (page 15, lines 281-382).

(9) Line 380 - the claim that MGIG weakens the interaction between HSD11b1 and SREBP2 cannot be made solely based on one Western blot.

Thank you for this important comment. We agree that the conclusion that MgIG weakens the interaction between HSD11B1 and SREBP2 should not be based solely on a single co-IP/Western blot experiment. In the revised manuscript, we have therefore toned down this statement to more appropriately reflect the data. Specifically, we now describe this result as a preliminary observation suggesting a potential modulation of the interaction, rather than a definitive conclusion. Please refer to Page 15, line 391.

(10) It's not clear what the numbers represent on top of the Western blots. Are these averages over the course of three independent experiments?

Thank you for this helpful comment. We apologize for the lack of clarity in the original figure presentation. The numbers shown above the Western blot bands represent the densitometric quantification of protein expression normalized to GAPDH, calculated from three independent experiments. However, this information was not clearly specified in the original figure, which may have led to confusion. To address this concern, we have now revised the manuscript by explicitly clarifying the meaning of these values in the figure legends. In addition, we have added bar graphs showing the quantified results from three independent experiments for Figures S3A, S4D, S6B, and S8H to improve transparency and data presentation.

(11) The claim in line 382 that knockdown of Hsd11b1 resulted in accumulation of pSREBP2 is not supported by the data provided in Figure 6D.

Thank you for pointing out this issue. We sincerely apologize for the incorrect description in the original manuscript. This was a wording error. We have made the revision on page 15, line394-396.

(12) None of the images provided in Figure 6E support the claims stated in the results. Activation of SREBP2 leads to nuclear translocation and subsequent induction of genes involved in cholesterol biosynthesis and uptake. Manipulation of Hsd11b1 via OE or KD does not show any nuclear localization with DAPI.

Thank you for this important comment. We agree that the original description was not sufficiently clear, which may have led to misunderstanding of the results. To clarify, Figure 6E includes two experimental contexts. Under basal (physiological) conditions in AML-12 cells, manipulation of Hsd11b1 (overexpression or knockdown) does not significantly affect the subcellular distribution of SREBP2. However, under EtOH/PA-induced stress conditions, Hsd11b1 overexpression promotes both nuclear and cytoplasmic levels of SREBP2, whereas Hsd11b1 knockdown reduces SREBP2 expression in both compartments. We have made the revision on page 16, line399.

(13) The entire manuscript is focused on this axis of MgIG-Hsd11b1-Srebp2, but no Srebp2 transcriptional targets are ever measured.

We sincerely appreciate this great suggestion. We have made the necessary revisions as suggested on page 12, lines 285-288, line 292 by adding the mRNA changes of Lcn2 and Ldlr, which are SREBP2 target genes. As requested, we have added the required information to Figures 1F and 1H.

(14) Acc1 and Scd1 are Srebp1 targets, not Srebp2.

Thank you for this important comment. We agree that Acc1 and Scd1 are well-established downstream target genes of SREBP1 rather than SREBP2. To better support our proposed SREBP2-related mechanism, we further examined canonical SREBP2 downstream target genes, including Lcn2 and Ldlr. The results are consistent with activation of SREBP2 signaling in our model. These data have now been included in the revised manuscript (Page 12, Lines 285–288 and 292; Figures 1F and 1H).

(15) A major weakness of this manuscript is the lack of studies providing quantitative assessments of Srebp2 activation and true liver lipid measurements.

Thank you for this important comment. We acknowledge the concern regarding the lack of direct quantitative assessment of SREBP2 activation in the original version of the manuscript. To address this limitation, we have strengthened the evidence supporting SREBP2 activation using multiple complementary approaches. Specifically, we assessed the expression of canonical SREBP2 downstream target genes (Page 12, Lines 285–288 and 292; Figures 1F and 1H), together with Western blot analysis (Figure 6D) and immunofluorescence staining (Figure 6F), which collectively support activation of SREBP2 signaling in the EtOH/PA-induced ALD model.

In addition, to provide a more comprehensive evaluation of hepatic lipid accumulation, we measured serum TG and TC levels, as well as hepatic TG and TC content. These biochemical analyses further confirm the presence of significant lipid accumulation in our model. We have made the necessary revisions as suggested on page 12, lines 285-288 (Figure 1G).

Reviewer #2 (Public review):

(1) In Supplemental Figure 1A, all the treatment arms (A-control, MgIG-25 mg/kg, MgIG-50 mg/kg) showed body weight loss compared to the untreated controls. However, Figure 1E showed body weight gain in the treatment arms (A-control and MgIG-25 mg/kg), why? In Supplemental Figure 1A, the mice with MgIG (25 mg/kg) showed the lowest body weight, compared to either A-control or MgIG (50 mg/kg) treatment. Can the authors explain why MgIG (25 mg/kg) causes bodyweight loss more than MgIG (50 mg/kg)? What about the other parameters (ALT, ALS, NAS, etc.) for the mice with MgIG (50 mg/kg)?

We agree that this observation does not strictly follow a dose-dependent pattern. In vivo responses to pharmacological interventions, particularly in metabolic and liver disease models, are not always linear. The relatively greater body weight reduction observed in the 25 mg/kg group may be influenced by inter-individual variability, differences in metabolic adaptation, or sample size–related variation. Importantly, these differences in body weight were not statistically significant. Therefore, we selected the 50 mg/kg dose for subsequent animal experiments, as it demonstrated more consistent and stable improvements across multiple parameters, including body weight, ALT, AST, TG, and TC.

(2) IL-6 is a key pro-inflammatory cytokine significantly involved in ALD, acting as a marker of ALD severity. Can the authors explain why MgIG 1.0 mg/ml shows higher IL-6 gene expression than MgIG (0.1-0.5 mg/ml)? Same question for the mRNA levels of lipid metabolic enzymes Acc1 and Scd1.

Thank you for this important comment. We agree that IL-6, as well as lipid metabolism–related genes such as Acc1 and Scd1, are key indicators in ALD. The relatively higher expression observed at 1.0 mg/mL MgIG compared to lower concentrations (0.1–0.5 mg/mL) may be related to experimental constraints associated with the MgIG formulation used in this study.

Specifically, to maintain consistency with our in vivo experiments, we used a clinically available liquid formulation of MgIG (5 mg/mL), which is approved for intravenous administration in China. Due to its relatively low stock concentration, achieving higher working concentrations (e.g., 1.0 mg/mL) in vitro required a larger volume of the MgIG solution, thereby proportionally reducing the volume of culture medium. This reduction in effective culture conditions may adversely affect hepatocyte viability and function.

Supporting this, our CCK-8 and LDH assays indicated that higher MgIG concentrations were associated with subtle cytotoxicity or impaired cell status.

(3) For the qPCR results of Hsd11b1 knockdown (siRNA) and Hsd11b1 overexpression (plasmid) in AML-12 cells (Figure 5B), what is the description for the gene expression level (Y axis)? Fold changes versus GAPDH? Hsd11b1 overexpression showed non-efficiency (20-23, units on Y axis), even lower than the Hsd11b1 knockdown (above 50, units on Y axis). The authors need to explain this. For the plasmid-based Hsd11b1 overexpression, why does the scramble control inhibit Hsd11b1 gene expression (less than 2, units on the Y axis)? Again, this needs to be explained.

Thank you for this important comment, and we apologize for the lack of clarity in the Y-axis labeling, which may have led to misunderstanding.

As shown in Figures 5A and 5B, we have revised the Y-axis description to clearly indicate that gene expression levels are presented as relative expression normalized to GAPDH (fold change relative to the control group).

Recommendations for the authors:

Reviewer #1 (Recommendations for the authors):

(1) Use terms that show directionality to help the readers comprehend the data. For instance, Line 295 states MgIG treatment also modulated the expression.... In reality, MgIG treatment reduced the expression of those genes relative to ethanol-fed control mice.

Thank you very much for this precious suggestion. We have thoroughly revised this part as ‘In line with the observed histological and physiological improvements, MgIG treatment also reduced the expression of genes involved in lipid synthesis metabolism (Srebp1, Srebp2, Acc1, and Scd1, Lcn2, and Ldlr), inflammation (Tnf-α and Il-6), and pro-apoptosis (Bax) while restored the level of anti-apoptotic gene (Bcl2) in the liver tissue of EtOH mice (Fig. 1G-1H).’. Please refer to page 12, lines 290-294.

(2) Oil Red O staining is subjective and nonspecific. The authors make a claim that serum TGs are an indicator of liver function; however, measurement of hepatic TGs would be a better measure here and more consistent with the ORO staining.

We sincerely appreciate this great suggestion. We have made the necessary revisions as suggested on page 12, lines 285-288 as ‘Notably, significant differences were observed between the EtOH group and the MgIG-treated (EtOH+M) group in serum levels of liver enzymes (ALT and AST), serum lipid parameters (TG and TC), as well as Liver TG and TC contents—-key indicators of liver function and lipid metabolism.’. As requested, we have added the required information to Figures 1G.

(3) The focus of the paper is on this SREBP2 axis. However, in Figure 1, the authors do not show any SREBP2 target genes. This would be helpful in interpreting SREBP2 activity. Further, hepatic free cholesterol levels would also strengthen these data.

We sincerely appreciate this great suggestion. We have made the necessary revisions as suggested on page 12, lines 285-288, line 292 by adding the mRNA changes of Lcn2 and Ldlr, which are SREBP2 target genes. As requested, we have added the required information to Figures 1F and 1H.

(4) Labels showing directionality on the volcano plots in Figures 2A, B would be of great help here. It's unclear which groups are on the left or right.

Thank you very much! The authors have revised Figures 2A-C as requested. Please refer to the new version of Figures 2A-C.

(5) Ensure consistency in what is written in the results and the figure legends. See Figure 2 volcano plots for examples. The volcano plot in Figure 2B has no figure legend.

We thank the reviewer for the valuable suggestion. Accordingly, we have revised the legend for Figures 2B as suggested.

(6) Ensure consistency in the nomenclature. In some cases, the authors use ALD+MgIG, and in others, they just use MgIG. My recommendation would be to use Ctrl, EtOH, EtOH+M.

We sincerely appreciate this great suggestion. We have made the necessary revisions as suggested on page 6, lines 111-112, page 11, line 280 and page 12, line 282, 284, 293, 298, 301.

(7) The gene enrichment analysis in Figure 2C should also include some text about directionality, either in the figure or the figure legend. Upregulated DEGs in the MgIG group? It's unclear.

We thank the reviewer for the valuable suggestion. Accordingly, we have revised the legend for Figures 2C as suggested.

(8) The authors should consider shuffling the order of some of the figures for better transitions from one panel to the next. For instance, Figure 3B, C shows cell viability responses before showing the siRNA and OE are effective in knocking down and overexpressing their protein of interest.

We thank the reviewer for the valuable suggestion. Accordingly, we have revised the legend for Figures 3B and 3C as suggested.

(9) The authors need to be consistent in the colors that are used in the figures. It's incredibly hard to follow, as presented.

We appreciate the reviewer's comment regarding color consistency. In response, we have carefully revised all figures to ensure consistent use of colors across the manuscript. The updated versions are shown in Figures 3, 6, and 7.

(10) For Nile Red staining, multiple images at a lower objective need to be shown and/or cellular triglycerides and cholesterol levels should be quantified.

We appreciate the reviewer's insightful comment regarding the Nile Red staining. In response, we have quantified triglyceride and total cholesterol levels in the cell supernatant, which are now presented on page 12, line 285-287 and Figures 2F. Furthermore, we have included additional Nile Red staining images at a lower objective in Supplementary Figures 2D, 3B, 4C to better illustrate the lipid droplet distribution.

(11) Line 362 refers to Figure 4 when it should refer to Figure 5.

Thank you very much! The authors have revised on page 14, line 364.

(12) qPCR should be performed on canonical Srebp2 targets throughout the manuscript to tie in the MgG treatment with changes in sterol sensing and Srebp2.

Thank you for your valuable suggestion. The results are now included on page 12, lines 292 and 311, and the corresponding data in Figures 1H and 2G have been enhanced accordingly.

Reviewer #2 (Recommendations for the authors):

(1) The statement, figure labeling, and figure legend for Figure 1A-C are confused. The MgIG dosing on the X-axis for Figure 2D is missing.

Thank you for the correction. We have revised this problem. Please refer to the new version of Figure 1A-C and Figure 2D.

(2) Figure 3E is not well described in the main text and figure legend. What are those numbers on top of the blotting bands? It was guessed that the numbers were the mean for each group. But where is the SD or SE for each group? It is hard to tell the statistical significance without showing SD or SE. The same question applies to Figure 5E, Figure 56C-6D, and Figure 7G.

We sincerely appreciate this great suggestion. We have made the necessary revisions as suggested on page 13, lines 317-322. As suggested, we have added the required information to Figures S3A, S4D, S6B and S8H.

Version 2

Abstract

While magnesium isoglycyrrhizinate (MgIG) is a clinically approved therapy for alcohol-associated liver disease (ALD), its precise molecular targets and mechanisms remain uncharacterized. This study aimed to define MgIG’s hepatoprotective actions in chronic-binge ALD mouse models and ethanol/palmitic acid-exposed AML-12 hepatocytes. Through an integrated strategy encompassing RNA sequencing, molecular docking, and microscale thermophoresis, we discovered that MgIG directly binds to hydroxysteroid 11-beta dehydrogenase 1 (HSD11B1) at residue 187, a finding corroborated by molecular dynamics simulations. In vivo, MgIG markedly attenuated alcohol-induced liver injury, evidenced by ameliorated histological damage, reduced hepatic steatosis, and normalized liver-to-body weight ratios. In vitro, it effectively reduced lipid accumulation, inflammation, and apoptosis. Mechanistically, RNA sequencing identified isopentenyl diphosphate delta isomerase 1 (IDI1) as a key downstream effector. Hepatocyte-specific genetic manipulations confirmed that MgIG modulates the SREBP2-IDI1 axis, thereby suppressing lipogenesis, inflammatory responses, and apoptotic pathways. We reveal HSD11B1 as a novel direct molecular target of MgIG and elucidate its therapeutic mechanism through the HSD11B1-SREBP2-IDI1 signaling axis, which profoundly impacts ALD pathogenesis. These findings not only validate MgIG’s clinical utility but also highlight a promising new therapeutic target for ALD.

Introduction

Alcohol-associated liver disease (ALD) encompasses a spectrum of hepatic pathologies ranging from steatosis to fibrosis, cirrhosis, and ultimately, hepatocellular carcinoma, contributing significantly to the global burden of disease and premature mortality 1,2. With alcohol use disorder affecting approximately 283 million individuals worldwide (5.1% of the population), alcohol emerges as a leading cause of cirrhosis, conferring a 260-fold increased risk of liver-related death 3. Excessive alcohol consumption, the primary etiological factor in ALD, triggers a cascade of pathological events, including oxidative stress, inflammation, and lipid metabolism dysregulation 4. Current ALD management primarily focuses on alcohol abstinence and supportive care. While potential therapeutic targets, such as oxidative stress pathways, inflammatory cascades, and the gut-liver axis, have been extensively investigated, the identification of druggable hepatic signaling pathways remains elusive 5,6.

Hydroxysteroid 11-beta dehydrogenase 1 (HSD11B1), a cortisol-regenerating enzyme predominantly expressed in the liver and kidneys, elevates endogenous glucocorticoids and has been implicated in the pathogenesis of metabolic dysfunction-associated steatotic liver disease (MASLD) and liver fibrosis 7,8. Similarly, isopentenyl diphosphate delta isomerase 1 (IDI1), a cytoplasmic enzyme involved in lipid metabolism, has been identified as a key risk factor for hepatocellular carcinoma 9 and intrahepatic cholestasis 10. Emerging evidence suggests that exercise may ameliorate MASLD by downregulating IDI1 expression 11. However, the precise roles of HSD11B1 and IDI1 in ALD progression remain to be elucidated.

Magnesium isoglycyrrhizinate (MgIG), a fourth-generation glycyrrhizin (GL) derivative and a magnesium salt of a single stereoisomer (Fig. 1A), exhibits enhanced pharmacological properties compared to its predecessors. As an 18α-GL, MgIG possesses greater lipophilicity than the β-isomer, facilitating superior binding to target cell receptors and steroid hormones 12. This enhanced binding capacity translates to potent anti-inflammatory effects and antioxidant effects 13. MgIG has demonstrated therapeutic efficacy in various liver diseases, including drug-induced liver injury (DILI) 14, MASLD 15, and liver fibrosis 16. Notably, MgIG has been preliminarily shown to inhibit ethanol-induced activation of the hedgehog signaling pathway in hepatocytes 17 and attenuate acute alcohol-induced hepatic steatosis in a zebrafish model by modulating lipid metabolism-related gene expression 18. Furthermore, MgIG has been recognized by the Chinese Society of Hepatology for its clinical utility in ALD treatment 19. Despite its therapeutic promise and proven safety, the precise molecular targets of MgIG in the liver remain poorly defined, hindering the development of optimized treatment strategies for ALD. This study employed in vivo and in vitro ALD models to investigate the hepatoprotective mechanisms of MgIG, revealing its direct interaction with HSD11B1 as a key mediator of its therapeutic effects and the involvement of downstream signaling of the sterol regulatory element binding protein 2 (SREBP2)-IDI1 axis.

MgIG alleviates liver damage in a mouse model of chronic-binge alcoholic liver disease (the NIAAA model).

(A) Chemical structure of MgIG. (B) Flowchart illustrating the modeling process for the NIAAA model. IP, intraperitoneal injections. (C) Representative results of H&E and Oil Red O staining from the livers of mice in Ctrl, EtOH and EtOH+M groups (n = 5). (D) Alterations in NAS (NAFLD activity score) and Oil Red O quantification (a.v.: arbitrary value) (n = 5). (E) Ratios of liver weight to body weight (LW/BW) in mice (n = 5). (F) Alterations in serum biochemical parameters (ALT, AST, TG, and TC) in mice in three groups (n = 5). (G) Alterations in liver parameters (TG and TC) in mice in three groups (n = 5). (H) Alterations in mRNA expression of lipid metabolism genes (Srebp1, Srebp2, Acc1,Scd1, Lcn2, and Ldlr), systemic inflammation markers (Tnf-α, Il1b, Il-6, and Il-16), and apoptosis-related genes (Bax and Bcl2) in the mice liver. The data are presented as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001, ****P < 0.0001. Scale bar: 50 μm.

Methods

Chemicals and reagents

MgIG was generously provided by Chia-Tai Tianqing Pharmaceutical Group Co., Ltd. (Nanjing, China) in the form of a magnesium isoglycyrrhizinate injection (5 mg/mL). High-purity ethanol was obtained from MACKLIN (Shanghai, China). Palmitic acid (PA) and fatty acid-free bovine serum albumin (BSA) were purchased from Sigma-Aldrich (St. Louis, MO, USA). All cell culture reagents and consumables were obtained from Gibco (Carlsbad, CA, USA) or Corning Incorporated (Corning, NY, USA). Primary antibodies against tumor necrosis factor-α (TNF-α, #11948), interleukin-6 (IL-6, #12912), glyceraldehyde-3-phosphate dehydrogenase (GAPDH, #2118S), Bax (#2772S), Bcl-2 (#3498S), and hemagglutinin (HA, #3724S) were purchased from Cell Signaling Technology (Shanghai, China). Antibodies against IDI1 (#11166-2-AP) and SREBP2 (#28212-1-AP) were obtained from Proteintech (Wuhan, China). An antibody against HSD11B1 (#AF3397) was purchased from R&D Systems (Minneapolis, MN, USA). A Flag antibody (F1804) was purchased from Sigma-Aldrich. All antibody validation experiments were performed according to the manufacturers’ protocols. Protein A/G Magarose beads (#80105G) were purchased from Invitrogen (Carlsbad, CA, USA).

Animal experiments

Male C57BL/6 wild-type mice (7 weeks old; 19-21 g) were purchased from Guangzhou Qingle Biosciences Co., Ltd. (Guangzhou, China). Mice were acclimated to the housing environment for one week prior to experimental procedures. Alcoholic liver injury was induced using a modified National Institute on Alcohol Abuse and Alcoholism (NIAAA) model 20. Briefly, mice (n = 4 per group) were initially fed ad libitum with the control (Ctrl) Lieber-DeCarli liquid diet for 5 days to facilitate acclimation. Subsequently, the ALD groups (designated as ‘EtOH’ and ‘EtOH+M’ in figures) received the Lieber-DeCarli diet containing 5% (v/v) ethanol for 10 days, while the control group (designated as ‘Ctrl’ in figures) received an isocaloric control diet. Body weight and food intake were monitored daily. On day 11, ethanol-fed mice and their pair-fed controls were administered a single dose of ethanol (5 g/kg body weight) or an isocaloric maltose dextrin solution, respectively, via oral gavage in the early morning. Mice were euthanized 9 h later (Fig. 1B). A vehicle-MgIG control group was not included in this study because: (1) MgIG is a clinically approved drug with an established safety profile; (2) the dosage used in this study was calculated based on human clinical dosages using a standard conversion formula; and (3) the vehicle safety of MgIG with similar dose has been previously confirmed in an animal study 21. For viral infections, mice (n = 5 per group) received tail vein injections of 5 × 1011 genome copies of either AAV8 control or AAV-shRNA/plasmid. After 14 days, mice were fasted for 4 h at the end of the dark cycle and then euthanized to confirm hepatic upregulation or downregulation of Hsd11b1, Srebp2, or Idi1. These mice were then subjected to the NIAAA model and/or MgIG administration as described above. Target gene expression in the liver was verified using quantitative PCR and Western blotting. All experimental procedures were approved by the Ethical Committee of Jinan University, China (IACUC-20220708-04).

RNA sequencing and functional enrichment analysis

Total RNA was extracted from liver tissue samples using TRIzol reagent (Invitrogen) following the manufacturer’s instructions. RNA quality was assessed using a Nanodrop ONE spectrophotometer (Thermo Fisher, Waltham, MA, USA). Samples with A260/A280 ratios above 1.8 and A260/A230 ratios above 2.0 were deemed acceptable for further processing. RNA integrity was evaluated using an Agilent 2200 TapeStation (Agilent Technologies, Santa Clara, CA, USA), and only samples with an RNA integrity number above 7.0 were used for library preparation. Ribosomal RNA (rRNA) was depleted from total RNA using the Epicentre Ribo-Zero rRNA Removal Kit (Illumina) and fragmented to an average size of 200 bp. First-strand and second-strand cDNA synthesis, followed by adapter ligation and low-cycle enrichment, were performed using the NEBNext Ultra RNA Library Prep Kit for Illumina (New England Biolabs, Ipswich, MA, USA). Library quality was assessed using the Agilent 2200 TapeStation and Qubit 2.0 fluorometer (Thermo Fisher). Libraries were diluted to 10 pmol/L and subjected to cluster generation on a pair-end flow cell, followed by sequencing (2 × 150 bp) on an Illumina HiSeq 3000. Raw sequencing reads were processed to remove adapter sequences, low-quality reads, and reads containing poly-N stretches. Clean reads were aligned to the mouse reference genome using HISAT2 with default parameters. Gene expression levels were quantified using HTSeq, and differential expression analysis was performed using DESeq with read counts as input. The Benjamini-Hochberg method was used to adjust p-values for multiple testing. Differentially expressed genes (DEGs) were defined as those with a fold change > 2 and an adjusted p-value < 0.05. Heatmap visualization and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analysis were performed using the identified DEGs. A p-value < 0.05 was considered statistically significant for KEGG pathway enrichment.

Biochemical and cytokine analyses of mice serum and cell supernatants

Serum or hepatic levels of alanine aminotransferase (ALT), aspartate aminotransferase (AST), triglyceride (TG) and total cholesterol (TC) were measured using BK2800 (BIOBASE, Jinnan, China). Cell supernatants cytokine levels were determined by using corresponding ELISA kits from R&D Systems (TNF-α: #VAL609; IL-6: #VAL604G).

Liver tissue histology

Liver tissue samples were fixed in 10% neutral buffered formalin and subsequently embedded in paraffin. Tissue sections (5 μm thickness) were prepared and stained with hematoxylin and eosin (H&E) and Oil Red O for histological examination. Images were acquired using a LEICA Qwin Image Analyzer (Leica Microsystems, Milton Keynes, UK). The nonalcoholic fatty liver disease activity score (NAS) was determined for each group as previously described 22.

Cell culture and transfection

The AML-12 mouse normal hepatocyte cell line was obtained from the Cell Bank of Type Culture Collection, Chinese Academy of Sciences (Shanghai, China). Cells were cultured in Dulbecco’s modified Eagle’s medium supplemented with 10% (v/v) fetal bovine serum, incubated at 37 °C with 5% CO2 in a cell incubator. To induce an ALD-like phenotype in AML-12 cells, cells were exposed to a combination of 25 mmol/L ethanol and 0.1-1 mmol/L palmitic acid (PA; Sigma-Aldrich; #P0500) for 24 h to determine the optimal concentration for inducing cellular injury, as previously described (12). We chose the combination of ethanol and palmitic acid in the in vitro experiments because ethanol-only treatment could not phenocopy alcoholic cell death, inflammation, oxidative stress, and the dysregulated lipid metabolism in hepatocytes exhibited in early-stage ALD 23-26. Following this initial treatment, varying concentrations of MgIG were added to the culture medium for an additional 24-hour to assess its effects and determine the optimal dose. For gene knockdown and overexpression experiments, Lipofectamine 3000 reagent (Thermo Fisher; #L3000001) was used to transfect AML-12 cells with Hsd11b1 or Idi1-targeting constructs in 6-well plates.

Cell lipid accumulation, viability, and apoptosis assays

Intracellular lipid droplets were visualized by staining AML-12 cells with Nile Red. Briefly, cells were washed with phosphate-buffered saline (PBS), fixed with 4% formaldehyde for 10 min, and then stained with Nile Red solution (0.1 mg/mL; #N8440, Solarbio, Beijing, China) for 10 min at room temperature in the dark. Cells were then counterstained with DAPI (5 μg/mL; Sigma-Aldrich; D9542) for 5 min. Cell viability and apoptosis were assessed in 96-well plates using a CCK8 cell viability assay and a lactate dehydrogenase (LDH) cytotoxicity assay kit, respectively, according to the manufacturer’s instructions (MedChem Excess, Shanghai, China; HY-K1090 and HY-K0301).

Quantitative PCR

Total RNA was extracted from liver tissue or cultured cells using TRIzol reagent. The first strand cDNA was synthesized from total RNA using a PrimeScript RT Reagent Kit (Takara, Shiga, Japan; #RR047A) following the manufacturer’s instructions. Quantitative PCR reaction was performed with the SYBR Premix Taq Quantitative PCR Kit (Takara) according to the manufacturer’s instructions, on a qTOWER3 machine (Analytik Jena AG, Jena, Germany). Primer information is as listed in Supporting Information Table S1. β-actin was used as an internal control. The relative quantification of mRNA expression levels was calculated using the 2-ΔΔCt method. All qPCR experiments were conducted in compliance with the MIQE guidelines 27.

Protein extraction and Western blot

Samples were lysed using Pierce RIPA buffer (Thermo Fisher) and their protein concentrations were measured with the Bio-Rad Protein Assay (Bio-Rad, Hercules, CA). Western blot analyses of all proteins were conducted with β-actin serving as the internal control.

Coimmunoprecipitation (Co-IP)

Co-IP buffer (50 mM Tris-HCl, 5 mM EDTA, 150 mM NaCl, and 1% NP-40 pH 7.6) mixed with protease inhibitor cocktail (Roche, Bern, Switzerland) were used to lyse the cells. The samples were then incubated with the corresponding antibodies and Protein A/G Magarose beads at 4°C overnight.

Protein structure modeling and molecular docking

We first employed DecoupleR’s 28 built-in Univariate Linear Model (ULM) to compute the transcription factor activity perturbed by MgIG, based on the expression of differentially expressed genes. The findings revealed that Srebf2 was the transcription factor most significantly reduced by MgIG. We then identified potential SREBP2/IDI1-interacting proteins using the STRING and PubMed databases. The 3D structures of these proteins were obtained from the Protein Data Bank (PDB) or UniProt, while the 3D structure of MgIG was retrieved from PubChem. Molecular docking simulations were performed using Schrödinger software to predict the binding affinity (Glide score) of MgIG to each protein. The lowest-energy docking conformations were visualized using PyMOL.

Microscale thermophoresis (MST) assay

The binding interaction between MgIG and HSD11B1 was assessed using a Monolith NT.115 Blue/Green instrument (NanoTemper Technologies, Munich, Germany). Initially, we evaluated the affinity and labeling efficiency of the dye with the His-tagged protein. Subsequently, HSD11B1 proteins (100 nM) were labeled and incubated with MgIG at a concentration gradient ranging from 50 µM to 1.53 nM for 30 min at room temperature. The samples were then analyzed at 60% MST power and a temperature of 25°C. Dissociation constants (Kd) were calculated based on a 1:1 binding stoichiometry.

Molecular dynamics (MD) simulations

Three molecular systems were constructed in this study: first, Compound-HSD11B complex was established through molecular docking. Second, the last frame from 100 ns MD simulation was used to generate APO-HSD11B1 by removing the ligand. Finally, based on this conformation and reported portal vein ethanol concentrations in ALD, five ethanol molecules (0.1 g/dL) were incorporated to construct the EtOH-HSD11B1 system, simulating the ALD environment 29-31. For each system, receptor was prepared and missing atoms of residues were fixed by the advanced PDB-Preparation tool in Yinfo Cloud Computing Platform using PDBFixer and the tLEaP module in AmberTools 20. The AM1-BCC charges were calculated for compound magnesium isoglycyrrhizinate by the Amber antechamber program 32. MD simulations was performed using AmberTools 20 package with AMBER ff19SB 33 and GAFF 34 force field.

The system was solvated by a truncated octahedron water box using OPC water model with a margin of 10 Å. Periodic boundary condition (PBC) was used and the net charge neutralized by Na+ ions. Nonbonded van der Waals interactions were calculated using the Lennard-Jones 12-6 potentials with a 10 Å cutoff, while long-range electrostatics were treated using the Particle Mesh Ewald (PME) algorithm. The SHAKE algorithm was applied to constrain bonds involving hydrogen atoms 35. To removed improper atom contacts, the structure was first minimized by (1) 2500 steps of steepest descent and 2500 steps of conjugate gradient, under a harmonic constraint of 10.0 kcal/(mol·Å2) on heavy atoms; (2) relaxing the entire system by 10000 steps of steepest descent and 10000 steps of conjugate gradient. And then the system was gradually heated up to 300 K by a 20 ps NVT simulation. Subsequently, two steps of equilibration phases were carried out: (1) a 200 ps NPT simulation with constraints on heavy atoms followed by (2) a 1 ns NVT simulation without restraint. The temperature was maintained at 300 K using the Berendsen thermostat with 1 ps coupling constant and the pressure at 1 atm using Monte Carlo barostat with 1 ps relaxation time. Finally, the system was subjected to a 100 ns NVT simulation with a time step of 2 fs. The root-mean-square deviation (RMSD), root-mean-square fluctuation (RMSF), radius of gyration (RG), solvent-accessible surface area (SASA) and hydrogen bonds were analyzed by the CPPTRAJ module, while principal component analysis (PCA) and dynamic cross-correlation matrix (DCCM) were analyzed by R package Bio3D 36. The binding free energies were calculated using the Molecular Mechanics Generalized Born (MM/PBSA) method for the 100 ns MD trajectory 37.

HSD11B1 enzyme activity assays

The enzyme activity of HSD11B1 in cells was evaluated according to its capability to convert cortisone to cortisol 38. AML-12 cells were seeded into 6-well culture plates and induced ALD as above. Different concentrations of MgIG (0.1, 0.25, and 0.5 mg/mL) were added 24 h prior to the co-treatment, with a control group included. AML-12 cells were exposed to 160 nmol/L cortisone for 24 h. The reaction mixtures were collected and analyzed for cortisol levels using an ELISA kit (R&D Systems, Minneapolis, MN, USA), according to the manufacturer’s instructions.

Statistical analysis

The data from each group are presented as the mean ± standard deviation (SD). For data that followed a normal distribution, statistical comparisons between two groups were conducted using an unpaired two-tailed Student’s t-test; for comparisons involving three or more groups, a two-way ANOVA followed by a Student-Newman-Keuls post hoc test was applied (Prism 5.0, Graphpad Software, Inc., San Diego, CA). A P-value of less than 0.05 was deemed statistically significant.

Results

MgIG alleviates liver injury in a mouse model of ALD

To investigate the hepatoprotective effects of MgIG in vivo, we employed a well-established chronic-binge NIAAA mouse model of ALD (Fig. 1B). Based on the drug’s clinical instructions, previous studies 21,39, and our preliminary experimental results (Fig. S1), we determined an optimal MgIG dose of 50 mg/kg. Compared to mice fed a normal diet (Ctrl group), mice in the alcohol-fed control group (EtOH) exhibited characteristic histological features of ALD, including steatosis and inflammatory cell infiltration, resulting in an elevated NAS. MgIG treatment (EtOH+M) effectively attenuated these pathological changes (Fig. 1C and 1D). Consistent with these histological findings, the liver-to-body weight ratio, a marker of liver injury, was significantly increased in the EtOH group, and this increase was markedly reduced by MgIG treatment (Fig. 1E). Notably, significant differences were observed between the EtOH group and the MgIG-treated (EtOH+M) group in serum levels of liver enzymes (ALT and AST), serum lipid parameters (TG and TC), as well as Liver TG and TC contents-key indicators of liver function and lipid metabolism. (Fig. 1F). In line with the observed histological and physiological improvements, MgIG treatment also reduced the expression of genes involved in lipid synthesis metabolism (Srebp1, Srebp2, Acc1, Scd1, Lcn2, and Ldlr), inflammation (Tnf-α and Il-6), and pro-apoptosis (Bax) while restored the level of anti-apoptotic gene (Bcl2) in the liver tissue of EtOH mice (Fig. 1G-1H).

MgIG protects against ethanol-induced hepatocyte injury via IDI1

To further elucidate the molecular mechanisms underlying the hepatoprotective effects of MgIG, we performed RNA sequencing analysis on liver tissue from the NIAAA mouse model. DEG analysis revealed a significant upregulation of Idi1 in the EtOH group compared to the Ctrl group (Fig. 2A, Fig. S4A-4B). Furthermore, KEGG pathway enrichment analysis identified metabolic pathways among the top five downregulated pathways in the MgIG-treated group compared to the EtOH group, with Idi1 consistently ranked among the top two genes in these pathways (Fig. 2C). To further investigate the role of IDI1 and its potential interaction with MgIG, we established an in vitro model of ethanol/palmitic acid (EtOH/PA)-induced hepatocyte injury using AML-12 cells. We first optimized the EtOH/PA concentrations to induce significant cell death and lipid accumulation (Fig. S2), identifying 250 mmol/L ethanol and 0.2 mmol/L PA as the optimal combination (Fig. S2A-2C). MgIG treatment (0.1-1.0 mg/mL) demonstrated a dose-dependent protective effect against EtOH/PA-induced injury, as evidenced by improved cell viability, reduced lipid accumulation, and decreased apoptosis (Fig. 2D-2G, Fig. S2D). Consistent with the in vivo findings, EtOH/PA treatment increased the expression of genes involved in lipid metabolism (Srebp1, Acc1, Scd1, Srebp2, Lcn2, and Ldlr) and inflammation (Tnf-α and Il-6), and MgIG treatment effectively reversed these effects (Fig. 2H). Based on these results, we selected 0.25 mg/mL as the optimal MgIG concentration for subsequent in vitro experiments.

MgIG protects ethanol-induced hepatocyte injury in a cell model.

(A) Volcano plot analysis showing differentially expressed genes between the EOH group and the Ctrl group after RNA-seq in the liver of mice. (B) Volcano plot analysis showing differentially expressed genes between the EtOH+M and the EtOH group after RNA-seq in liver of mice. (C) The top 5 regulated pathways (both up- and down-regulated) and the top 3 genes within each pathway are shown (EtOH+M vs EtOH).. (D) Changes in AML-12 cell viability, apoptosis, and Nile Red staining signals after ethanol/PA treatment, with or without co-treatment with different MgIG doses (EtOH+M) (0, 0.1, 0.25, 0.5, and 1 mg/mL) (n = 4). (E) Representative images of Nile Red staining in AML-12 cells treated with ethanol/PA, with or without co-treatment with different MgIG doses. (F)Quantification of triglyceride (TG) and total cholesterol (TC) levels in the in the culture supernatant of AML-12 cells treated with EtOH/PA in the presence or absence of increasing concentrations of MgIG (n = 4). (G-H) Changes in mRNA expression of lipid metabolism genes (Srebp1, Acc1,Scd1, Srebp2, Lcn2, and Ldlr) and systemic inflammation markers (Tnf-α and Il-6) in AML-12 cells treated with ethanol/PA, with or without co-treatment with different MgIG doses. Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001. Scale bar: 20 μm.

In line with the in vivo observations, Idi1 expression was significantly increased in AML-12 cells following EtOH/PA treatment, and this effect was attenuated by MgIG treatment (Fig. 3A and S3A-3C). As shown in Fig. 3B and 3C, transfection with siRNA and plasmid effectively decreased or increased Idi1 mRNA levels without affecting cell viability, respectively. Knockdown of Idi1 significantly ameliorated EtOH/PA-induced cell injury, as evidenced by reduced apoptosis, inflammatory cytokine production, and lipid accumulation. In contrast, Idi1 overexpression tended to exacerbate these pathological changes (Fig. 3D-3H, Fig. S3). Although the effects of Idi1 overexpression on apoptosis and inflammatory cytokines did not reach statistical significance in Western blot analyses, Idi1 overexpression markedly attenuated the hepatoprotective effects of MgIG (Fig. 3E, Fig. S3A). One possible explanation is that Idi1 functions as a permissive factor in EtOH/PA-induced hepatocellular injury, rather than acting as a sole or rate-limiting determinant. In this context, modulation of Idi1 may be necessary to facilitate lipid metabolic reprogramming and stress responses, but is not sufficient on its own to fully dictate cell fate decisions such as apoptosis or survival. This interpretation is consistent with the multifactorial nature of ALD, which involves the coordinated interplay of oxidative stress, inflammatory signaling, and metabolic dysregulation 5,6. Given that MgIG has been reported to exert broad anti-inflammatory and antioxidant effects13, it is likely that its hepatoprotective actions are mediated through multiple parallel pathways, with Idi1 representing one important, but not exclusive, target. Taken together, these findings suggest that MgIG protects against ethanol-induced hepatocyte injury, at least in part, through the modulation of IDI1.

IDI1 is involved in MgIG-mediated hepatocyte protection against ethanol.

(A) Quantitative PCR validation of RNA-seq results revealed changes in Idi1 gene expression in AML-12 cells treated with ethanol/PA, with or without 0.25 mg/mL MgIG co-treatment (EtOH/PA and EtOH/PA+M) (n = 4). (B) Quantitative PCR results confirmed the knockdown or overexpression efficiency of Idi1 genes by siRNA or Idi1 plasmid in AML-12 cells. (C) The changes in AML-12 cell viability following Idi1 siRNA or Idi1 plasmid transfection (24 h) were also assessed (n = 4). (D) Changes in cell viability and apoptosis ratios were assessed in ethanol/PA-treated AML-12 cells, with or without 0.25 mg/mL MgIG, following Idi1 knockdown/overexpression (n = 4). (E, F) Western blot results for TNF-α, IL-6, Bax, and Bcl-2 and cell supernatant results for TNF-α and IL-6 in AML-12 cells treated with ethanol/PA (EtOH/PA) and ethanol/PA + MgIG (EtOH/PA+M), with or without Idi1 knockdown/overexpression. Numbers above the lanes indicate the mean relative density normalized to the loading control for each group (n = 3). (G, H) Nile Red staining area (%) with corresponding representative cell staining images. Data are expressed as mean ± SD. For Western blot quantification: *P < 0.05, **P < 0.01, ***P < 0.001. Scale bar: 20 μm.

MgIG directly binds to HSD11B1

To identify potential direct binding partners of MgIG, we initially performed molecular docking simulations between MgIG and IDI1. However, the resulting Glide score of -2.74 indicated a lack of favorable binding interactions, which implied that there should be an immediate binding protein in the upstream of IDI1. To identify potential upstream regulators of Idi1 expression, we utilized the ULM within the DecoupleR package to analyze transcription factor activity. This analysis identified SREBP2 as the most significantly affected transcription factor (Fig. 4A). We then expanded our search to include upstream regulators of IDI1 identified using the STRING database. Among these proteins, HSD11B1 exhibited the highest binding affinity for MgIG, with a Glide score of -8.75 (Fig. 4B). Given the homology between human and mouse Hsd11b1 and the need for future translational research, we focused on validating the interaction between human HSD11B1 and MgIG. We conducted 100 ns MD simulations for Compound-HSD11B1 (MgIG-HSD11B1 binding in physiological condition) and EtOH-HSD11B1 (MgIG-HSD11B1 binding in alcoholic condition), with free HSD11B1 as a control. The results revealed that HSD11B1 exhibited high flexibility and dynamic motion in its unbound state but became significantly more rigid and stable upon binding to MgIG, particularly at residues 219–233 (Fig. 4C-4E). This structural stabilization was further supported by the radius of gyration curves, which indicated a more compact conformation upon binding (Fig. S5A and 5B). Further analyses, including PCA and DCCM, demonstrated alterations in motion direction, dynamic patterns, and residue correlations. Specifically, upon binding, HSD11B1 exhibited reduced motion amplitude and weaker residue correlations, with its dynamic patterns becoming more disordered (Fig. S5C-5E). In the Compound-HSD11B1 system (Fig. 4E), key interactions included hydrogen bonds (Tyr177, Tyr183), a salt bridge (Lys187) and hydrophobic interactions (Leu126, Leu217, Ala223, Ala226, and Ile230). In contrast, the EtOH-HSD11B1 system (Fig. 4F) exhibited hydrogen bonds (Thr124, Ser170, Tyr183, Leu217, and Arg269) along with an additional salt bridge (Tyr183 and Arg269). Notably, the EtOH-HSD11B1 system demonstrated stronger hydrogen bonding and more favorable binding free energy compared to the Compound-HSD11B1 system (Fig. 4G and S5F), suggesting enhanced stability and binding affinity in an ethanol environment. Based on molecular docking and MD results, we further validated the binding between MgIG and the human full-length wild-type (WT) HSD11B1 protein as well as its site-directed mutants (Tyr177, M1; Tyr183, M2; Lys187, M3) using MST. The Kd value of the WT protein was 6.35 μM (Fig. 4H), while those of M1, M2, and M3 were 48.6 μM, 11.5 μM, and 135.6 μM, respectively (Fig. 4I). These data indicate that MgIG primarily exerts its anti-ALD effect by inhibiting HSD11B1 through the critical Lys187 site.

HSD11B1 is the direct binding protein of MgIG for the protection of ethanol-induced hepatocytes injury.

(A) Bar chart displaying the top 10 upregulated and downregulated transcription factor activity scores in the EtOH+M group compared to the EtOH group. (B) The glide score of MgIG binding to the protein structure as determined by molecular docking analysis. (C, D) RMSD and RMSF analysis of the three systems: APO-HSD11B1 (blue) represents unbound HSD11B1 in a physiological saline system, Compound-HSD11B1 (red) represents HSD11B1 bound to MgIG in a physiological saline system, and EtOH-HSD11B1 (green) represents HSD11B1 bound to MgIG in a 0.1 mg/mL ethanol solvent system. (E, F) Molecular modeling analysis of MgIG binding at the HSD11B1 domain in normal saline and ethanol systems. Left: Cartoon view of MgIG at the HSD11B1 binding site. Right: Close-up surface view of MgIG at the HSD11B1 binding sites. (G) Hydrogen bond analysis of HSD11B1-MgIG interactions in normal saline and ethanol systems. (H, I) The microscale thermophoresis (MST) assay demonstrated direct binding between varying doses of MgIG and human HSD11B1 protein at residues 187. WT: wild-type HSD11B1; M1, M2, M3: point mutations at Tyr177, Tyr183, and Lys187, respectively.

To further investigate the functional significance of this interaction, we modulated Hsd11b1 expression in AML-12 cells using siRNA- and plasmid-mediated knockdown and overexpression, respectively. As shown in Fig. 5A-5C, transfection with siRNA and plasmid effectively decreased or increased Hsd11b1 mRNA levels without affecting cell viability, respectively. Knockdown of Hsd11b1 significantly attenuated EtOH/PA-induced inflammation, apoptosis, and lipid accumulation, even in the absence of MgIG treatment. Conversely, overexpression of Hsd11b1 exacerbated these effects. Importantly, MgIG treatment partially reversed the detrimental effects of Hsd11b1 overexpression (Fig. 5D-5F, Fig S4C-4D). To further investigate whether the binding of MgIG to HSD11B1 affects its enzymatic activity, we added different concentrations of MgIG (0.1, 0.25, and 0.5 mg/mL) to the cellular model. ELISA results showed that HSD11B1 activity was significantly elevated in the ALD group, whereas increasing concentrations of MgIG led to a dose-dependent reduction in HSD11B1 activity (Fig. 5G).Given the low basal activity under normal conditions, we further examined cortisol levels in the supernatant of AML-12 cells overexpressing Hsd11b1, with or without MgIG co-treatment (Fig. 5H). These findings suggested that MgIG exerted its protective effects against EtOH/PA-induced hepatocyte injury, at least in part, by directly binding to and modulating the activity of HSD11B1.

HSD11B1 is involved in MgIG-mediated hepatocyte protection against ethanol.

(A) Quantitative PCR validation of RNA-seq results revealed changes in Hsd11b1 gene expression in AML-12 cells treated with ethanol/PA, with or without 0.25 mg/mL MgIG co-treatment (EtOH/PA and EtOH/PA+M) (n = 4). (B, C) Quantitative PCR confirmed the knockdown efficiency of Hsd11b1 (siRNA) and the overexpression efficiency of Hsd11b1(plasmid) in AML-12 cells, and cell viability changes were assessed 48 h after transfection (n = 4). (D) Nile Red staining area (%) with corresponding representative cell staining images (n=4). (E, F) Western blot results for TNF-α, IL-6, Bax, and Bcl-2 and cell supernatant results for TNF-α and IL-6 in AML-12 cells treated with ethanol/PA (EtOH/PA) and ethanol/PA + MgIG (EtOH/PA+M), with or without Hsd11b1 knockdown/overexpression. Numbers above the lanes indicate the mean relative density normalized to the loading control for each group (n = 3). (G,H) Impact of MgIG on Hsd11b1 Activity. Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001. Scale bar: 20 μm.

MgIG protects hepatocyte partially through the HSD11B1–SREBP2–IDI1 axis

To investigate the relationship between SREBP2 and HSD11B1, we conducted co-IP experiments, which revealed a direct interaction between the precursor form of SREBP2 (p-SREBP2) and HSD11B1 (Fig. S4E-4F). This interaction appeared to be reduced following MgIG treatment. (Fig. 6A and 6B). To further explore this interaction, we modulated Hsd11b1 expression in EtOH/PA induced AML-12 cells with or without MgIG treatment (Fig. 6C-6D, Fig. S6). Knockdown of Hsd11b1 reduced nuclear translocation of SREBP2 (n-SREBP2), while Hsd11b1 overexpression promoted the accumulation of n-SREBP2, an effect further enhanced by the EtOH/PA treatment. These findings suggest that HSD11B1 may regulate the processing and nuclear translocation of SREBP2 in in vivo ALD model. Immunofluorescent analysis confirmed these observations (Fig. 6E). As shown in Fig. 6F, the co-IP results indicated that HSD11B1 also interacted with its downstream protein IDI1. In addition, the dual-luciferase reporter assay demonstrated that Srebp2 positively regulates Idi1 expression (Fig. 6G). In in vivo experiments, it was confirmed that in normal liver tissue, the expression of Srebp2 and Idi1 followed a similar trend in response to overexpression or knockdown of Hsd11b1 (Fig. 6H and 6I). Knockdown of Srebp2 resulted in a decrease in Idi1 expression, without affecting Hsd11b1 levels. Conversely, neither knockdown nor overexpression of Idi1 influenced the expression of the upstream genes Hsd11b1 or Srebp2. In liver tissue from ALD, the expression changes of upstream and downstream genes upon overexpression or knockdown of Hsd11b1 or Idi1 mirrored those seen in normal liver tissue. However, Srebp2 knockdown induced a negative feedback effect, reducing Hsd11b1 expression, which was not observed in normal liver tissue (Fig. 6J and 6K).

MgIG exerts its protective effect via the HSD11B1-SREBP2-IDI1 axis in ALD model.

(A, B) Co-IP was used to verify the direct binding between HSD11B1 and SREBP2 with or without MgIG treatment. (C, D) Alterations in protein levels of HSD11B1, p-SREBP2, n-SREBP2, and IDI1 in AML-12 cells induced by EtOH/PA, following knockdown or overexpression of Hsd11b1, with and without MgIG treatment. Numbers above the lanes indicate the mean relative density normalized to the loading control for each group (n = 3). (E) Immunofluorescent staining was conducted to visualize the distribution and expression of SREBP2 (red) in EtoH/PA-induced AML-12 cells, with or without MgIG, following Hsd11b1 knockdown or overexpression. (F) Co-IP was used to verify the direct binding between HSD11B1 and IDI1. (G) Effects of Srebp2 on Idi1 transcriptional regulation were measured by luciferase assays in AML-12 and 293T cell lines. Idi1-wild-type (WT) or Idi1-mutant (Mut), plasmids with WT promoter cDNA clone of Idi1 or with mutant promoter cDNA clone plasmid; pRL-TK, an internal control reporter plasmid. (H, I) The expression levels of Hsd11b1, Srebp2, and Idi1 in normal liver were measured following the knockdown of Hsd11b1, Srebp2, and Idi1, or the overexpression of Hsd11b1 and Idi1, respectively (n = 4). (J, K) The expression levels of Hsd11b1, Srebp2, and Idi1 in ALD liver were measured following the knockdown of Hsd11b1, Srebp2, and Idi1, or the overexpression of Hsd11b1 and Idi1, respectively (n = 5). Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001. ****P < 0.0001. Scale bar: 10 μm.

To further investigate the roles of HSD11B1, SREBP2, and IDI1 in the in vivo ALD model, we used AAV8-mediated shRNA delivery to knock down their expression or employed overexpression plasmids to increase their expression specifically in hepatocytes. As shown in Fig. S6A-6C, knockdown or overexpression of Hsd11b1 or Idi1 in mice fed a normal control diet did not result in significant changes in liver histology, lipid accumulation, or serum ALT and AST levels (Fig. S7). However, in the ALD model, knockdown of Hsd11b1, Srebp2, or Idi1 attenuated ethanol-induced liver injury, as evidenced by improved histological NAS scores, reduced steatosis, and decreased inflammation. MgIG treatment further enhanced these beneficial effects. Conversely, overexpression of Hsd11b1 or Idi1 abolished the therapeutic effects of MgIG on ethanol-induced liver injury (Fig. 7A-7F and S8). Interestingly, modulation of Idi1 expression did not affect the expression of Hsd11b1 or Srebp2, suggesting that IDI1 acts downstream of HSD11B1 and SREBP2. In contrast, modulation of Hsd11b1 expression altered the levels of n-SREBP2 and IDI1 (Fig. S8E-H), confirming that HSD11B1 regulates the SREBP2-IDI1 pathway. Collectively, these data indicate that MgIG protects against ALD, at least in part, by modulating the HSD11B1-SREBP2-IDI1 axis.

MgIG alleviates ALD-induced liver injury via the HSD11B1-SREBP2-IDI1 axis.

(A-D) Representative liver H&E and Oil Red O staining results from ALD mice with Hsd11b1, Srebp2, or Idi1 knockdown or overexpression, with and/or without MgIG co-treatment. Changes in quantitative NAS (NAFLD activity score) and Oil Red staining (area %) were calculated and analyzed (n = 5). (E-F) Changes of serum ALT and TNF-α from ALD mice with Hsd11b1, Srebp2, or Idi1 knockdown or overexpression, with and/or without MgIG co-treatment (n = 5). (G) Alterations in protein levels of HSD11B1, p-SREBP2, n-SREBP 2, and Idi1 in ALD mice, following knockdown or overexpression of Hsd11b1, with and without MgIG co-treatment. Numbers above the lanes indicate the mean relative density normalized to the loading control for each group (n = 3). Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001, ****P < 0.0001. Scale bar: 50 μm.

Discussion

While previous research using a zebrafish model demonstrated that MgIG alleviates alcohol-induced liver injury by modulating lipid metabolism-related gene expression 18, the precise molecular mechanisms and direct targets of MgIG remained unclear. This lack of mechanistic understanding hindered the development of optimized therapeutic strategies for ALD. In this study, we provide compelling evidence that MgIG effectively ameliorates key features of ALD, including hepatic steatosis, inflammation, and apoptosis, in both in vivo and in vitro models. Our findings shed light on the complex interplay of molecular pathways involved in ALD pathogenesis and highlight the therapeutic potential of targeting the HSD11B1-SREBP2-IDI1 axis.

Our RNA sequencing analysis identified IDI1 as a key player in ALD pathogenesis and a critical mediator of MgIG’s hepatoprotective effects. IDI1, an enzyme in the mevalonate pathway, is involved in the biosynthesis of isoprenoids, which are essential for various cellular processes, including cholesterol synthesis. Dysregulation of cholesterol metabolism is a hallmark of ALD, contributing to the accumulation of lipids in the liver. Our findings demonstrate that Idi1 expression is significantly upregulated in the livers of mice subjected to the NIAAA model of ALD, suggesting that increased IDI1 activity may contribute to the development of hepatic steatosis. Genetic manipulation of Idi1 expression further confirmed its role in ALD. Specifically, Idi1 knockdown protected against alcohol-induced liver injury, an effect further enhanced by MgIG treatment. This suggests that reducing IDI1 activity can ameliorate the detrimental effects of alcohol on the liver and that MgIG may exert its therapeutic benefits, at least in part, by suppressing IDI1. Conversely, Idi1 overexpression abolished the therapeutic benefits of MgIG, both in vivo and in vitro, highlighting the importance of IDI1 in mediating MgIG’s effects. These findings are consistent with recent reports highlighting the role of IDI1 in hepatic cholesterol accumulation and lipid toxicity 40 41 and its involvement in hepatocellular carcinoma progression via inhibition of the cGAS-STING pathway 9. Furthermore, our study identified SREBP2, a master regulator of lipid metabolism, as an upstream regulator of IDI1. SREBP2 belongs to a family of transcription factors that control the expression of genes involved in cholesterol and fatty acid biosynthesis. SREBP2 has been implicated in various aspects of liver pathology, including NLRP3 inflammasome activation 42, lipid accumulation 43, liver cancer progression 44, with its target protein IDI1 upregulated in parallel 30. Our findings demonstrate that both SREBP2 and IDI1 are upregulated in response to EtOH/PA treatment and that MgIG effectively inhibits their expression, consistent with the notion that SREBP2 contributes to the development of MASLD 45. The identification of SREBP2 as a key regulator of IDI1 in the context of ALD provides a mechanistic link between lipid metabolism and the pathogenesis of this disease.

To identify the direct molecular target of MgIG, we employed a combination of molecular docking, MD, MST analysis, and genetical manipulation studies. These approaches converged on HSD11B1, a key enzyme in glucocorticoid metabolism, as a high-affinity binding partner of MgIG. HSD11B1 catalyzes the conversion of inactive cortisone to active cortisol in the liver, thereby increasing intracellular glucocorticoid levels. Glucocorticoids are steroid hormones that play a critical role in regulating glucose and lipid metabolism, and their dysregulation has been implicated in the development of metabolic disorders, including type 2 diabetes 46. As a potential inhibitor of HSD11B1 47, GL can improve patients’ insulin and lipid levels 48. In addition, the increased expression of Hsd11b1 enhances the enzymatic reducing activity, promoting a fat-forming phenotype in cell models through elevated cortisol levels 49,50. Meanwhile, Hsd11b1 deficiency prevents hepatic steatosis in high-fat diets-fed mice 51. Our findings demonstrate that MgIG directly binds to the Lys187 of HSD11B1 and that modulation of Hsd11b1 expression in hepatocytes significantly influences the development of ALD.

While some studies have suggested a potential pro-fibrotic role for HSD11B1 inhibition 8, our findings, along with those of other recent studies 7,51,52, support a protective role for Hsd11b1 knockdown in the context of alcoholic liver injury. These discrepancies may be attributed to differences in experimental models and the specific cell types targeted. For instance, the study by Zou et al 8 examined the effects of global Hsd11b1 deficiency, which could trigger compensatory activation of the hypothalamic-pituitary-adrenal axis or paracrine regulatory mechanisms, potentially affecting the pro-fibrotic response. In contrast, our study focused on hepatocyte-specific Hsd11b1 knockdown, which may avoid these confounding factors. Importantly, our study provides evidence for a novel HSD11B1-SREBP2-IDI1 axis in the pathogenesis of ALD. We demonstrate that HSD11B1 regulates the processing and nuclear translocation of SREBP2, which in turn controls the expression of IDI1. Notably, this is consistent with previous studies showing that increased SREBP2 expression and nuclear translocation activate the NLRP3 inflammasome and the mevalonate pathway, thereby promoting inflammation and tumor progression 53,54. This regulatory axis appears to be a key target of MgIG’s therapeutic effects. By directly binding to HSD11B1, MgIG may inhibit its activity, leading to reduced SREBP2 activation and subsequent downregulation of IDI1. This, in turn, could contribute to the observed improvements in hepatic steatosis, inflammation, and apoptosis 55-57.

This study provides mechanistic evidence that MgIG directly targets HSD11B1 and modulates the HSD11B1–SREBP2– IDI1 axis to attenuate ALD. However, several limitations should be acknowledged. First, our findings are derived from preclinical mouse models and hepatocyte systems, and pharmacokinetics, biodistribution, and long-term safety of MgIG remain to be comprehensively evaluated in larger and more diverse populations. Second, although molecular docking and thermophoresis confirmed direct binding of MgIG to HSD11B1, high-resolution structural studies such as X-ray crystallography or cryo-electron microscopy are needed to delineate the precise binding interface and conformational changes. Third, other signaling pathways potentially influenced by MgIG have not been systematically explored and may contribute to its therapeutic effects. Future work should focus on validating these findings in human tissues, optimizing MgIG dosing strategies, and conducting multicenter clinical trials to assess its translational potential and establish HSD11B1 as a druggable target for precision therapy in ALD.

eLife Assessment

This important study reports characterisation of hepatocyte molecular pathways affected by a glycyrrhizin derivative in both in vivo and in vitro mouse models of alcohol-associated liver disease. The authors show convincing evidence indicating that IPP delta isomerase 1 (Idi1) is an intermediate in these pharmacological effects, via the binding of the glycyrrhizin derivative to an upstream regulator of Idi1, HSD11B1, although significant questions remain about some of the experiments and analyses provided. The findings would be of interest to immunologists and pharmacologists interested in liver inflammation and its amelioration.

Reviewer #1 (Public review):

Summary:

In this article by Xiao et al. the authors aimed to identify the precise targets by which magnesium isoglycyrrhizinate (MgIG) functions to improve liver injury in response to ethanol treatment. The authors found through a series of in-vivo and molecular approaches that MgIG treatment attenuates alcohol-induced liver injury through a potential SREBP2-IdI1 axis. The revised manuscript adds to a previous set of literature showing MgIG improves liver function across a variety of etiologies, and also provides mechanistic insight into its mechanism of action. All major weaknesses were addressed in the revised submission.

Strengths:

(1) The authors use a combination of approaches from both in-vivo mouse models to in-vitro approaches with AML12 hepatocytes to support the notion that MgIG does improve liver function in response to ethanol treatment.

(2) The authors use both knockdown and overexpression approaches, in-vivo and in-vitro, to support most of the claims provided.

(3) Identification of HSD11B1 as the protein target of MgIG, as well as confirmation of direct protein-protein interactions between HSD11B1/SREBP2/IDI1 is novel.

Weaknesses:

The authors addressed all my concerns.

Reviewer #2 (Public review):

Summary:

In this manuscript, the authors investigated magnesium isoglycyrrhizinate (MgIG)'s hepatoprotective actions in chronic-binge alcohol-associated liver disease (ALD) mouse models and ethanol/palmitic acid-challenged AML-12 hepatocytes. They found that MgIG markedly attenuated alcohol-induced liver injury, evidenced by ameliorated histological damage, reduced hepatic steatosis, and normalized liver-to-body weight ratios. RNA sequencing identified isopentenyl diphosphate delta isomerase 1 (IDI1) as a key downstream effector. Hepatocyte-specific genetic manipulations confirmed that MgIG modulates the SREBP2-IDI1 axis. The mechanistic studies suggested that MgIG could directly target HSD11B1 and modulate the HSD11B1-SREBP2-IDI1 axis to attenuate ALD. This manuscript is of interest to the research field of ALD.

Strengths:

The authors have performed both in vivo and in vitro studies to demonstrate the action of magnesium isoglycyrrhizinate on hepatocytes and an animal model of alcohol-associated liver disease.

Original comment (1):

In Supplemental Figure 1A, all the treatment arms (A-control, MgIG-25 mg/kg, MgIG-50 mg/kg) showed body weight loss compared to the untreated controls. However, Figure 1E showed body weight gain in the treatment arms (A-control and MgIG-25 mg/kg), why? In Supplemental Figure 1A, the mice with MgIG (25 mg/kg) showed the lowest body weight, compared to either A-control or MgIG (50 mg/kg) treatment. Can the authors explain why MgIG (25 mg/kg) causes bodyweight loss more than MgIG (50 mg/kg)? What about the other parameters (ALT, ALS, NAS, etc.) for the mice with MgIG (50 mg/kg)?

Author's response:

We agree that this observation does not strictly follow a dose-dependent pattern. In vivo responses to pharmacological interventions, particularly in metabolic and liver disease models, are not always linear. The relatively greater body weight reduction observed in the 25 mg/kg group may be influenced by inter-individual variability, differences in metabolic adaptation, or sample size-related variation. Importantly, these differences in body weight were not statistically significant. Therefore, we selected the 50 mg/kg dose for subsequent animal experiments, as it demonstrated more consistent and stable improvements across multiple parameters, including body weight, ALT, AST, TG, and TC.

New comment:

My first question: All the treatment arms (A-control, MgIG-25 mg/kg, MgIG-50 mg/kg) showed significant body weight loss compared to the untreated controls (Supplemental Figure 1A), but the body weight significantly increased in the treatment arms (A-control and MgIG-50 mg/kg) compared to the untreated controls (Figure 1E). Why?

My second question: Mice with MgIG (25 mg/kg) showed the lowest body weight, compared to either A-control or MgIG (50 mg/kg) treatment. According to the authors' explanation, the MgIG (25 mg/kg) caused bodyweight loss are attributed to inter-individual variability, differences in metabolic adaptation, or sample size-related variation. Did these differences happen in MgIG (25 mg/kg) only? or in all other groups? The mouse group assignment should be randomized; however, a large variation in bodyweight was seen in MgIG (25 mg/kg) group. It is not convincing for the author to select MgIG (50 mg/kg) group for subsequent animal experiments, because of a large variation in MgIG (25 mg/kg) group, and because that MgIG (50 mg/kg) group demonstrated more consistent and stable improvements across multiple parameters. The author should reanalyze and compare all the raw data between MgIG (50 mg/kg) group and MgIG (25 mg/kg) group, and address the issues being pointed out and justify rationale for the animal group assignment.

Original comment (2):

IL-6 is a key pro-inflammatory cytokine significantly involved in ALD, acting as a marker of ALD severity. Can the authors explain why MgIG 1.0 mg/ml shows higher IL-6 gene expression than MgIG (0.1-0.5 mg/ml)? Same question for the mRNA levels of lipid metabolic enzymes Acc1 and Scd1.

Author's response:

Thank you for this important comment. We agree that IL-6, as well as lipid metabolism-related genes such as Acc1 and Scd1, are key indicators in ALD. The relatively higher expression observed at 1.0 mg/mL MgIG compared to lower concentrations (0.1-0.5 mg/mL) may be related to experimental constraints associated with the MgIG formulation used in this study. Specifically, to maintain consistency with our in vivo experiments, we used a clinically available liquid formulation of MgIG (5 mg/mL), which is approved for intravenous administration in China. Due to its relatively low stock concentration, achieving higher working concentrations (e.g., 1.0 mg/mL) in vitro required a larger volume of the MgIG solution, thereby proportionally reducing the volume of culture medium. This reduction in effective culture conditions may adversely affect hepatocyte viability and function. Supporting this, our CCK-8 and LDH assays indicated that higher MgIG concentrations were associated with subtle cytotoxicity or impaired cell status.

New comment:

The author's response did not answer my question. If the authors believe it could be experimental constraints associated with the MgIG formulation, then it is questionable for this MgIG formulation used in all other associated experiments. The experiments, at least those the MgIG formulation associated experiments, need to be repeated.

Original comment (3):

For the qPCR results of Hsd11b1 knockdown (siRNA) and Hsd11b1 overexpression (plasmid) in AML-12 cells (Figure 5B), what is the description for the gene expression level (Y axis)? Fold changes versus GAPDH? Hsd11b1 overexpression showed non-efficiency (20-23, units on Y axis), even lower than the Hsd11b1 knockdown (above 50, units on Y axis). The authors need to explain this. For the plasmid-based Hsd11b1 overexpression, why does the scramble control inhibit Hsd11b1 gene expression (less than 2, units on the Y axis)? Again, this needs to be explained.

Author's response:

Thank you for this important comment, and we apologize for the lack of clarity in the Y-axis labeling, which may have led to misunderstanding.

As shown in Figures 5A and 5B, we have revised the Y-axis description to clearly indicate that gene expression levels are presented as relative expression normalized to GAPDH (fold change relative to the control group).

New comment:

The author explained the relative expression was normalized to GAPDH (fold change), but they did not answer my question. My question is for Figure 5B. in Figure 5B (left, Hsd11b1-KD), scramble control showed over 100 (unit), however, in Figure 5B (right, Hsd11b1-OE), scramble control showed only 0.5-1 (unit). The data seemed that authors used same scramble control for both KD and OE? If yes, they should provide more details of the KD and OE experiments and explain why this happened. If they used plasmid for OE control, they also need to clarify it. In addition, qPCR is not a good assay to show the success of KD or OE, Western blotting should be done as convincing data to show the success of KD or OE.

Author response:

The following is the authors’ response to the previous reviews

Public Reviews:

Reviewer #1 (Public review):

The authors addressed all my concerns.

We sincerely appreciate your recognition of our efforts to address the reviewers' suggestions and improve the manuscript.

Reviewer #2 (Public review):

(1) All the treatment arms (A-control, MgIG-25 mg/kg, MgIG-50 mg/kg) showed significant body weight loss compared to the untreated controls (Supplemental Figure 1A), but the body weight significantly increased in the treatment arms (A-control and MgIG-50 mg/kg) compared to the untreated controls (Figure 1E). Why?

We appreciate the reviewer’s careful observation regarding the apparent discrepancy between Supplemental Figure 1A and Figure 1E. We apologize for any confusion caused by the presentation of these data.

We would like to clarify that Supplemental Figure 1A and Figure 1E represent two different parameters. Supplemental Figure 1A shows absolute body weight, whereas Figure 1E presents the liver-to-body weight ratio (LW/BW), as indicated in the revised figure legend.

In the NIAAA alcohol-fed model, chronic ethanol exposure typically results in reduced body weight gain or relative body weight loss compared with normal diet-fed control mice, which is consistent with the findings shown in Supplemental Figure 1A. In the preliminary dose-finding study, all alcohol-fed groups (EtOH groups, MgIG 25 mg/kg, and MgIG 50 mg/kg) exhibited lower absolute body weight compared with the untreated control group, which is a common feature of ethanol-induced liver injury models.

By contrast, Figure 1E reflects changes in the LW/BW ratio rather than total body weight. Ethanol feeding induces hepatomegaly and hepatic steatosis, thereby increasing the LW/BW ratio. Although the LW/BW ratio in the MgIG-treated group remained higher than that in the untreated control group, MgIG treatment significantly reduced the ethanol-induced increase in LW/BW ratio compared with the EtOH group, consistent with its hepatoprotective effects and reduced hepatic lipid accumulation. We hope this clarification could well answer this concern. Thank you very much!

(2) Mice with MgIG (25 mg/kg) showed the lowest body weight, compared to either A-control or MgIG (50 mg/kg) treatment. According to the authors' explanation, the MgIG (25 mg/kg) caused bodyweight loss are attributed to inter-individual variability, differences in metabolic adaptation, or sample size-related variation. Did these differences happen in MgIG (25 mg/kg) only? or in all other groups? The mouse group assignment should be randomized; however, a large variation in bodyweight was seen in MgIG (25 mg/kg) group. It is not convincing for the author to select MgIG (50 mg/kg) group for subsequent animal experiments, because of a large variation in MgIG (25 mg/kg) group, and because that MgIG (50 mg/kg) group demonstrated more consistent and stable improvements across multiple parameters. The author should reanalyze and compare all the raw data between MgIG (50 mg/kg) group and MgIG (25 mg/kg) group, and address the issues being pointed out and justify rationale for the animal group assignment.

We appreciate the reviewer’s careful evaluation regarding the variability observed in the MgIG (25 mg/kg) group and the rationale for dose selection.

Supplemental Figure 1A presents data from our preliminary dose-finding study (n=5 per group, independent cohort), in which all alcohol-fed groups showed expected body weight loss relative to the normal-diet control, as is typical in the NIAAA model. The 25 mg/kg group exhibited numerically greater variability (likely due to inter-individual metabolic differences and small sample size), but no statistically significant difference was observed among the three alcohol-fed groups (A-control, 25 mg/kg, and 50 mg/kg) in final body weight (one-way ANOVA with post-hoc test).

Mice were randomized by initial body weight and age prior to diet feeding. To address the reviewer’s concern, we have now included Supplementary Table Body weight-raw data with individual animal body weight data (raw values, mean ± SD) for both the dose-finding and main experiments, together with statistical comparisons. We selected 50 mg/kg for all subsequent experiments because it provided more consistent and statistically significant improvements across multiple key parameters (ALT, AST, TG, TC, NAS score, Oil Red O staining, and LW/BW ratio) compared with 25 mg/kg. The 25 mg/kg group showed greater variability in several indices, which is why it was not chosen for mechanistic studies.

To further clarify this point, we have added detailed descriptions of the randomization procedure and dose-selection rationale in the revised Methods section. Please refer to Page 5, line 106-108 and Page 10, line 276-277. In addition, we will provide the original data on mouse body weight changes, together with the corresponding statistical analyses, in the supplementary materials to further enhance transparency and facilitate reference.

(3) The author's response did not answer my question. If the authors believe it could be experimental constraints associated with the MgIG formulation, then it is questionable for this MgIG formulation used in all other associated experiments. The experiments, at least those the MgIG formulation associated experiments, need to be repeated.

We sincerely appreciate the reviewer’s concern regarding the potential impact of the MgIG formulation on the reliability of the associated experiments.

As clarified in our previous response, the commercially available MgIG preparation used in this study is a clinically approved injectable formulation (5 mg/mL). During the preliminary in vitro dose-ranging experiments, achieving the highest testing concentration (1.0 mg/mL) required the addition of a relatively larger volume of stock solution, which slightly reduced the effective culture medium volume and may have contributed to minor effects on cell status. Consistently, CCK-8 and LDH assays showed a slight reduction in cell viability only at the highest concentration tested.

Importantly, this phenomenon was observed exclusively in the 1.0 mg/mL group. All subsequent functional and mechanistic experiments were performed using the optimized non-toxic concentration (0.25 mg/mL), at which MgIG consistently and significantly improved IL-6, Acc1, Scd1, and other relevant parameters in a dose-dependent manner (P < 0.05), without detectable cytotoxicity.

In addition, vehicle controls with volume-matched conditions were included for the high-concentration (1 mg/mL) condition to exclude potential confounding effects caused by solvent volume differences. The protective effects observed at 0.25 mg/mL were highly reproducible and were further supported by multiple independent lines of evidence, including RNA-seq analysis, enzyme activity assays, and knockdown/overexpression experiments, all of which demonstrated consistent mechanistic trends.

Therefore, we believe that the current data obtained using the optimized concentration remain reliable and interpretable, and that the formulation-related issue observed at the highest concentration does not affect the validity of the main conclusions. Nevertheless, to further address the reviewer’s concern, we are willing to provide additional replicate data for the 1.0 mg/mL cell viability/toxicity assays, as well as repeat qPCR analyses under volume-matched vehicle control conditions in the Supplementary File . Please refer to Supplementary Figure 2E.

(4) The author explained the relative expression was normalized to GAPDH (fold change), but they did not answer my question. My question is for Figure 5B. in Figure 5B (left, Hsd11b1-KD), scramble control showed over 100 (unit), however, in Figure 5B (right, Hsd11b1-OE), scramble control showed only 0.5-1 (unit). The data seemed that authors used same scramble control for both KD and OE? If yes, they should provide more details of the KD and OE experiments and explain why this happened. If they used plasmid for OE control, they also need to clarify it. In addition, qPCR is not a good assay to show the success of KD or OE, Western blotting should be done as convincing data to show the success of KD or OE.

We apologize that our previous response did not fully clarify the details of Figure 5B. The left panel of Figure 5B shows the Hsd11b1 knockdown experiment using Hsd11b1 siRNA with scramble siRNA as the corresponding control, whereas the right panel shows the Idi1 overexpression experiment using the Idi1 expression plasmid with empty vector as the corresponding control. These are two independent experiments with separate control groups, rather than a shared scramble control. We recognize that the labeling and figure presentation may have caused confusion, we have revised the legend for Figures 3B, 3C and Figures 5B, 5C as suggested.

For both experiments, relative mRNA expression levels were normalized to GAPDH and analyzed independently using the 2^−ΔΔCt method relative to their respective controls. Therefore, the numerical values shown in the two panels are not directly comparable. The apparent difference in baseline expression levels reflects independent normalization and the intrinsic expression characteristics of different genes, rather than the use of the same control group or any data inconsistency.

We have confirmed that transfection efficiencies were consistent with expectations and did not significantly affect cell viability.

We also agree with the reviewer that protein-level validation would provide stronger evidence for the success of knockdown and overexpression. Accordingly, we have performed Western blot analyses for Hsd11b1 knockdown and Idi1 overexpression and will include these data in the revised manuscript to complement the qPCR results (Please refer to revised Supplementary Figure 3C and 4D).

Version 3

Abstract

While magnesium isoglycyrrhizinate (MgIG) is a clinically approved therapy for alcohol-associated liver disease (ALD), its precise molecular targets and mechanisms remain uncharacterized. This study aimed to define MgIG’s hepatoprotective actions in chronic-binge ALD mouse models and ethanol/palmitic acid-exposed AML-12 hepatocytes. Through an integrated strategy encompassing RNA sequencing, molecular docking, and microscale thermophoresis, we discovered that MgIG directly binds to hydroxysteroid 11-beta dehydrogenase 1 (HSD11B1) at residue 187, a finding corroborated by molecular dynamics simulations. In vivo, MgIG markedly attenuated alcohol-induced liver injury, evidenced by ameliorated histological damage, reduced hepatic steatosis, and normalized liver-to-body weight ratios. In vitro, it effectively reduced lipid accumulation, inflammation, and apoptosis. Mechanistically, RNA sequencing identified isopentenyl diphosphate delta isomerase 1 (IDI1) as a key downstream effector. Hepatocyte-specific genetic manipulations confirmed that MgIG modulates the SREBP2-IDI1 axis, thereby suppressing lipogenesis, inflammatory responses, and apoptotic pathways. We reveal HSD11B1 as a novel direct molecular target of MgIG and elucidate its therapeutic mechanism through the HSD11B1-SREBP2-IDI1 signaling axis, which profoundly impacts ALD pathogenesis. These findings not only validate MgIG’s clinical utility but also highlight a promising new therapeutic target for ALD.

Introduction

Alcohol-associated liver disease (ALD) encompasses a spectrum of hepatic pathologies ranging from steatosis to fibrosis, cirrhosis, and ultimately, hepatocellular carcinoma, contributing significantly to the global burden of disease and premature mortality 1,2. With alcohol use disorder affecting approximately 283 million individuals worldwide (5.1% of the population), alcohol emerges as a leading cause of cirrhosis, conferring a 260-fold increased risk of liver-related death 3. Excessive alcohol consumption, the primary etiological factor in ALD, triggers a cascade of pathological events, including oxidative stress, inflammation, and lipid metabolism dysregulation 4. Current ALD management primarily focuses on alcohol abstinence and supportive care. While potential therapeutic targets, such as oxidative stress pathways, inflammatory cascades, and the gut-liver axis, have been extensively investigated, the identification of druggable hepatic signaling pathways remains elusive 5,6.

Hydroxysteroid 11-beta dehydrogenase 1 (HSD11B1), a cortisol-regenerating enzyme predominantly expressed in the liver and kidneys, elevates endogenous glucocorticoids and has been implicated in the pathogenesis of metabolic dysfunction-associated steatotic liver disease (MASLD) and liver fibrosis 7,8. Similarly, isopentenyl diphosphate delta isomerase 1 (IDI1), a cytoplasmic enzyme involved in lipid metabolism, has been identified as a key risk factor for hepatocellular carcinoma 9 and intrahepatic cholestasis 10. Emerging evidence suggests that exercise may ameliorate MASLD by downregulating IDI1 expression 11. However, the precise roles of HSD11B1 and IDI1 in ALD progression remain to be elucidated.

Magnesium isoglycyrrhizinate (MgIG), a fourth-generation glycyrrhizin (GL) derivative and a magnesium salt of a single stereoisomer (Fig. 1A), exhibits enhanced pharmacological properties compared to its predecessors. As an 18α-GL, MgIG possesses greater lipophilicity than the β-isomer, facilitating superior binding to target cell receptors and steroid hormones 12. This enhanced binding capacity translates to potent anti-inflammatory effects and antioxidant effects 13. MgIG has demonstrated therapeutic efficacy in various liver diseases, including drug-induced liver injury (DILI) 14, MASLD 15, and liver fibrosis 16. Notably, MgIG has been preliminarily shown to inhibit ethanol-induced activation of the hedgehog signaling pathway in hepatocytes 17 and attenuate acute alcohol-induced hepatic steatosis in a zebrafish model by modulating lipid metabolism-related gene expression 18. Furthermore, MgIG has been recognized by the Chinese Society of Hepatology for its clinical utility in ALD treatment 19. Despite its therapeutic promise and proven safety, the precise molecular targets of MgIG in the liver remain poorly defined, hindering the development of optimized treatment strategies for ALD. This study employed in vivo and in vitro ALD models to investigate the hepatoprotective mechanisms of MgIG, revealing its direct interaction with HSD11B1 as a key mediator of its therapeutic effects and the involvement of downstream signaling of the sterol regulatory element binding protein 2 (SREBP2)-IDI1 axis.

MgIG alleviates liver damage in a mouse model of chronic-binge alcoholic liver disease (the NIAAA model).

(A) Chemical structure of MgIG. (B) Flowchart illustrating the modeling process for the NIAAA model. IP, intraperitoneal injections. (C) Representative results of H&E and Oil Red O staining from the livers of mice in Ctrl, EtOH and EtOH+M groups (n = 5). (D) Alterations in NAS (NAFLD activity score) and Oil Red O quantification (a.v.: arbitrary value) (n = 5). (E) Ratios of liver weight to body weight (LW/BW) in mice (n = 5). (F) Alterations in serum biochemical parameters (ALT, AST, TG, and TC) in mice in three groups (n = 5). (G) Alterations in liver parameters (TG and TC) in mice in three groups (n = 5). (H) Alterations in mRNA expression of lipid metabolism genes (Srebp1, Srebp2, Acc1,Scd1, Lcn2, and Ldlr), systemic inflammation markers (Tnf-α, Il1b, Il-6, and Il-16), and apoptosis-related genes (Bax and Bcl2) in the mice liver. The data are presented as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001, ****P < 0.0001. Scale bar: 50 μm.

Methods

Chemicals and reagents

MgIG was generously provided by Chia-Tai Tianqing Pharmaceutical Group Co., Ltd. (Nanjing, China) in the form of a magnesium isoglycyrrhizinate injection (5 mg/mL). High-purity ethanol was obtained from MACKLIN (Shanghai, China). Palmitic acid (PA) and fatty acid-free bovine serum albumin (BSA) were purchased from Sigma-Aldrich (St. Louis, MO, USA). All cell culture reagents and consumables were obtained from Gibco (Carlsbad, CA, USA) or Corning Incorporated (Corning, NY, USA). Primary antibodies against tumor necrosis factor-α (TNF-α, #11948), interleukin-6 (IL-6, #12912), glyceraldehyde-3-phosphate dehydrogenase (GAPDH, #2118S), Bax (#2772S), Bcl-2 (#3498S), and hemagglutinin (HA, #3724S) were purchased from Cell Signaling Technology (Shanghai, China). Antibodies against IDI1 (#11166-2-AP) and SREBP2 (#28212-1-AP) were obtained from Proteintech (Wuhan, China). An antibody against HSD11B1 (#AF3397) was purchased from R&D Systems (Minneapolis, MN, USA). A Flag antibody (F1804) was purchased from Sigma-Aldrich. All antibody validation experiments were performed according to the manufacturers’ protocols. Protein A/G Magarose beads (#80105G) were purchased from Invitrogen (Carlsbad, CA, USA).

Animal experiments

Male C57BL/6 wild-type mice (7 weeks old; 19-21 g) were purchased from Guangzhou Qingle Biosciences Co., Ltd. (Guangzhou, China). Mice were acclimated to the housing environment for one week prior to experimental procedures. Alcoholic liver injury was induced using a modified National Institute on Alcohol Abuse and Alcoholism (NIAAA) model 20. Randomization was performed by an investigator not involved in subsequent data collection and analysis using a random number table. Briefly, mice (n = 5 per group) were initially fed ad libitum with the control (Ctrl) Lieber-DeCarli liquid diet for 5 days to facilitate acclimation. Subsequently, the ALD groups (designated as ’EtOH’ and ’EtOH+M’ in figures) received the Lieber-DeCarli diet containing 5% (v/v) ethanol for 10 days, while the control group (designated as ’Ctrl’ in figures) received an isocaloric control diet. Body weight and food intake were monitored daily. On day 11, ethanol-fed mice and their pair-fed controls were administered a single dose of ethanol (5 g/kg body weight) or an isocaloric maltose dextrin solution, respectively, via oral gavage in the early morning. Mice were euthanized 9 h later (Fig. 1B). A vehicle-MgIG control group was not included in this study because: (1) MgIG is a clinically approved drug with an established safety profile; (2) the dosage used in this study was calculated based on human clinical dosages using a standard conversion formula; and (3) the vehicle safety of MgIG with similar dose has been previously confirmed in an animal study 21. For viral infections, mice (n = 5 per group) received tail vein injections of 5 × 1011 genome copies of either AAV8 control or AAV-shRNA/plasmid. After 14 days, mice were fasted for 4 h at the end of the dark cycle and then euthanized to confirm hepatic upregulation or downregulation of Hsd11b1, Srebp2, or Idi1. These mice were then subjected to the NIAAA model and/or MgIG administration as described above. Target gene expression in the liver was verified using quantitative PCR and Western blotting. All experimental procedures were approved by the Ethical Committee of Jinan University, China (IACUC-20220708-04).

RNA sequencing and functional enrichment analysis

Total RNA was extracted from liver tissue samples using TRIzol reagent (Invitrogen) following the manufacturer’s instructions. RNA quality was assessed using a Nanodrop ONE spectrophotometer (Thermo Fisher, Waltham, MA, USA). Samples with A260/A280 ratios above 1.8 and A260/A230 ratios above 2.0 were deemed acceptable for further processing. RNA integrity was evaluated using an Agilent 2200 TapeStation (Agilent Technologies, Santa Clara, CA, USA), and only samples with an RNA integrity number above 7.0 were used for library preparation. Ribosomal RNA (rRNA) was depleted from total RNA using the Epicentre Ribo-Zero rRNA Removal Kit (Illumina) and fragmented to an average size of 200 bp. First-strand and second-strand cDNA synthesis, followed by adapter ligation and low-cycle enrichment, were performed using the NEBNext Ultra RNA Library Prep Kit for Illumina (New England Biolabs, Ipswich, MA, USA). Library quality was assessed using the Agilent 2200 TapeStation and Qubit 2.0 fluorometer (Thermo Fisher). Libraries were diluted to 10 pmol/L and subjected to cluster generation on a pair-end flow cell, followed by sequencing (2 × 150 bp) on an Illumina HiSeq 3000. Raw sequencing reads were processed to remove adapter sequences, low-quality reads, and reads containing poly-N stretches. Clean reads were aligned to the mouse reference genome using HISAT2 with default parameters. Gene expression levels were quantified using HTSeq, and differential expression analysis was performed using DESeq with read counts as input. The Benjamini-Hochberg method was used to adjust p-values for multiple testing. Differentially expressed genes (DEGs) were defined as those with a fold change > 2 and an adjusted p-value < 0.05. Heatmap visualization and Kyoto Encyclopedia of Genes and Genomes (KEGG) pathway enrichment analysis were performed using the identified DEGs. A p-value < 0.05 was considered statistically significant for KEGG pathway enrichment.

Biochemical and cytokine analyses of mice serum and cell supernatants

Serum or hepatic levels of alanine aminotransferase (ALT), aspartate aminotransferase (AST), triglyceride (TG) and total cholesterol (TC) were measured using BK2800 (BIOBASE, Jinnan, China). Cell supernatants cytokine levels were determined by using corresponding ELISA kits from R&D Systems (TNF-α: #VAL609; IL-6: #VAL604G).

Liver tissue histology

Liver tissue samples were fixed in 10% neutral buffered formalin and subsequently embedded in paraffin. Tissue sections (5 μm thickness) were prepared and stained with hematoxylin and eosin (H&E) and Oil Red O for histological examination. Images were acquired using a LEICA Qwin Image Analyzer (Leica Microsystems, Milton Keynes, UK). The nonalcoholic fatty liver disease activity score (NAS) was determined for each group as previously described 22.

Cell culture and transfection

The AML-12 mouse normal hepatocyte cell line was obtained from the Cell Bank of Type Culture Collection, Chinese Academy of Sciences (Shanghai, China). Cells were cultured in Dulbecco’s modified Eagle’s medium supplemented with 10% (v/v) fetal bovine serum, incubated at 37 °C with 5% CO2 in a cell incubator. To induce an ALD-like phenotype in AML-12 cells, cells were exposed to a combination of 25 mmol/L ethanol and 0.1-1 mmol/L palmitic acid (PA; Sigma-Aldrich; #P0500) for 24 h to determine the optimal concentration for inducing cellular injury, as previously described (12). We chose the combination of ethanol and palmitic acid in the in vitro experiments because ethanol-only treatment could not phenocopy alcoholic cell death, inflammation, oxidative stress, and the dysregulated lipid metabolism in hepatocytes exhibited in early-stage ALD 23–26. Following this initial treatment, varying concentrations of MgIG were added to the culture medium for an additional 24-hour to assess its effects and determine the optimal dose. For gene knockdown and overexpression experiments, Lipofectamine 3000 reagent (Thermo Fisher; #L3000001) was used to transfect AML-12 cells with Hsd11b1 or Idi1-targeting constructs in 6-well plates.

Cell lipid accumulation, viability, and apoptosis assays

Intracellular lipid droplets were visualized by staining AML-12 cells with Nile Red. Briefly, cells were washed with phosphate-buffered saline (PBS), fixed with 4% formaldehyde for 10 min, and then stained with Nile Red solution (0.1 mg/mL; #N8440, Solarbio, Beijing, China) for 10 min at room temperature in the dark. Cells were then counterstained with DAPI (5 μg/mL; Sigma-Aldrich; D9542) for 5 min. Cell viability and apoptosis were assessed in 96-well plates using a CCK8 cell viability assay and a lactate dehydrogenase (LDH) cytotoxicity assay kit, respectively, according to the manufacturer’s instructions (MedChem Excess, Shanghai, China; HY-K1090 and HY-K0301).

Quantitative PCR

Total RNA was extracted from liver tissue or cultured cells using TRIzol reagent. The first strand cDNA was synthesized from total RNA using a PrimeScript RT Reagent Kit (Takara, Shiga, Japan; #RR047A) following the manufacturer’s instructions. Quantitative PCR reaction was performed with the SYBR Premix Taq Quantitative PCR Kit (Takara) according to the manufacturer’s instructions, on a qTOWER3 machine (Analytik Jena AG, Jena, Germany). Primer information is as listed in Supporting Information Table S1. β-actin was used as an internal control. The relative quantification of mRNA expression levels was calculated using the 2−ΔΔCt method. All qPCR experiments were conducted in compliance with the MIQE guidelines 27.

Protein extraction and Western blot

Samples were lysed using Pierce RIPA buffer (Thermo Fisher) and their protein concentrations were measured with the Bio-Rad Protein Assay (Bio-Rad, Hercules, CA). Western blot analyses of all proteins were conducted with β-actin serving as the internal control.

Coimmunoprecipitation (Co-IP)

Co-IP buffer (50LmM Tris-HCl, 5LmM EDTA, 150LmM NaCl, and 1% NP-40 pH 7.6) mixed with protease inhibitor cocktail (Roche, Bern, Switzerland) were used to lyse the cells. The samples were then incubated with the corresponding antibodies and Protein A/G Magarose beads at 4°C overnight.

Protein structure modeling and molecular docking

We first employed DecoupleR’s 28 built-in Univariate Linear Model (ULM) to compute the transcription factor activity perturbed by MgIG, based on the expression of differentially expressed genes. The findings revealed that Srebf2 was the transcription factor most significantly reduced by MgIG. We then identified potential SREBP2/IDI1-interacting proteins using the STRING and PubMed databases. The 3D structures of these proteins were obtained from the Protein Data Bank (PDB) or UniProt, while the 3D structure of MgIG was retrieved from PubChem. Molecular docking simulations were performed using Schrödinger software to predict the binding affinity (Glide score) of MgIG to each protein. The lowest-energy docking conformations were visualized using PyMOL.

Microscale thermophoresis (MST) assay

The binding interaction between MgIG and HSD11B1 was assessed using a Monolith NT.115 Blue/Green instrument (NanoTemper Technologies, Munich, Germany). Initially, we evaluated the affinity and labeling efficiency of the dye with the His-tagged protein. Subsequently, HSD11B1 proteins (100 nM) were labeled and incubated with MgIG at a concentration gradient ranging from 50 µM to 1.53 nM for 30 min at room temperature. The samples were then analyzed at 60% MST power and a temperature of 25°C. Dissociation constants (Kd) were calculated based on a 1:1 binding stoichiometry.

Molecular dynamics (MD) simulations

Three molecular systems were constructed in this study: first, Compound-HSD11B complex was established through molecular docking. Second, the last frame from 100 ns MD simulation was used to generate APO-HSD11B1 by removing the ligand. Finally, based on this conformation and reported portal vein ethanol concentrations in ALD, five ethanol molecules (0.1 g/dL) were incorporated to construct the EtOH-HSD11B1 system, simulating the ALD environment 29–31. For each system, receptor was prepared and missing atoms of residues were fixed by the advanced PDB-Preparation tool in Yinfo Cloud Computing Platform using PDBFixer and the tLEaP module in AmberTools 20. The AM1-BCC charges were calculated for compound magnesium isoglycyrrhizinate by the Amber antechamber program 32. MD simulations was performed using AmberTools 20 package with AMBER ff19SB 33 and GAFF 34 force field.

The system was solvated by a truncated octahedron water box using OPC water model with a margin of 10 Å. Periodic boundary condition (PBC) was used and the net charge neutralized by Na+ ions. Nonbonded van der Waals interactions were calculated using the Lennard-Jones 12-6 potentials with a 10 Å cutoff, while long-range electrostatics were treated using the Particle Mesh Ewald (PME) algorithm. The SHAKE algorithm was applied to constrain bonds involving hydrogen atoms 35. To removed improper atom contacts, the structure was first minimized by (1) 2500 steps of steepest descent and 2500 steps of conjugate gradient, under a harmonic constraint of 10.0 kcal/(mol·Å2) on heavy atoms; (2) relaxing the entire system by 10000 steps of steepest descent and 10000 steps of conjugate gradient. And then the system was gradually heated up to 300 K by a 20 ps NVT simulation. Subsequently, two steps of equilibration phases were carried out: (1) a 200 ps NPT simulation with constraints on heavy atoms followed by (2) a 1 ns NVT simulation without restraint. The temperature was maintained at 300 K using the Berendsen thermostat with 1 ps coupling constant and the pressure at 1 atm using Monte Carlo barostat with 1 ps relaxation time. Finally, the system was subjected to a 100 ns NVT simulation with a time step of 2 fs. The root-mean-square deviation (RMSD), root-mean-square fluctuation (RMSF), radius of gyration (RG), solvent-accessible surface area (SASA) and hydrogen bonds were analyzed by the CPPTRAJ module, while principal component analysis (PCA) and dynamic cross-correlation matrix (DCCM) were analyzed by R package Bio3D 36. The binding free energies were calculated using the Molecular Mechanics Generalized Born (MM/PBSA) method for the 100 ns MD trajectory 37.

HSD11B1 enzyme activity assays

The enzyme activity of HSD11B1 in cells was evaluated according to its capability to convert cortisone to cortisol 38. AML-12 cells were seeded into 6-well culture plates and induced ALD as above. Different concentrations of MgIG (0.1, 0.25, and 0.5 mg/mL) were added 24 h prior to the co-treatment, with a control group included. AML-12 cells were exposed to 160 nmol/L cortisone for 24 h. The reaction mixtures were collected and analyzed for cortisol levels using an ELISA kit (R&D Systems, Minneapolis, MN, USA), according to the manufacturer’s instructions.

Statistical analysis

The data from each group are presented as the mean ± standard deviation (SD). For data that followed a normal distribution, statistical comparisons between two groups were conducted using an unpaired two-tailed Student’s t-test; for comparisons involving three or more groups, a two-way ANOVA followed by a Student-Newman-Keuls post hoc test was applied (Prism 5.0, Graphpad Software, Inc., San Diego, CA). A P-value of less than 0.05 was deemed statistically significant.

Results

MgIG alleviates liver injury in a mouse model of ALD

To investigate the hepatoprotective effects of MgIG in vivo, we employed a well-established chronic-binge NIAAA mouse model of ALD (Fig. 1B). Based on the drug’s clinical instructions, previous studies 21,39, and our preliminary experimental results (including body weight change, serum ALT/AST, hepatic TG and TC levels, and histological NAS scores) (Fig. S1), we determined an optimal MgIG dose of 50 mg/kg. Compared to mice fed a normal diet (Ctrl group), mice in the alcohol-fed control group (EtOH) exhibited characteristic histological features of ALD, including steatosis and inflammatory cell infiltration, resulting in an elevated NAS. MgIG treatment (EtOH+M) effectively attenuated these pathological changes (Fig. 1C and 1D). Consistent with these histological findings, the liver-to-body weight ratio, a marker of liver injury, was significantly increased in the EtOH group, and this increase was markedly reduced by MgIG treatment (Fig. 1E). Notably, significant differences were observed between the EtOH group and the MgIG-treated (EtOH+M) group in serum levels of liver enzymes (ALT and AST), serum lipid parameters (TG and TC), as well as Liver TG and TC contents-key indicators of liver function and lipid metabolism. (Fig. 1F). In line with the observed histological and physiological improvements, MgIG treatment also reduced the expression of genes involved in lipid synthesis metabolism (Srebp1, Srebp2, Acc1, Scd1, Lcn2, and Ldlr), inflammation (Tnf-α and Il-6), and pro-apoptosis (Bax) while restored the level of anti-apoptotic gene (Bcl2) in the liver tissue of EtOH mice (Fig. 1G-1H).

MgIG protects against ethanol-induced hepatocyte injury via IDI1

To further elucidate the molecular mechanisms underlying the hepatoprotective effects of MgIG, we performed RNA sequencing analysis on liver tissue from the NIAAA mouse model. DEG analysis revealed a significant upregulation of Idi1 in the EtOH group compared to the Ctrl group (Fig. 2A, Fig. S4A-4B). Furthermore, KEGG pathway enrichment analysis identified metabolic pathways among the top five downregulated pathways in the MgIG-treated group compared to the EtOH group, with Idi1 consistently ranked among the top two genes in these pathways (Fig. 2C). To further investigate the role of IDI1 and its potential interaction with MgIG, we established an in vitro model of ethanol/palmitic acid (EtOH/PA)-induced hepatocyte injury using AML-12 cells. We first optimized the EtOH/PA concentrations to induce significant cell death and lipid accumulation (Fig. S2), identifying 250 mmol/L ethanol and 0.2 mmol/L PA as the optimal combination (Fig. S2A-2C). MgIG treatment (0.1-1.0 mg/mL) demonstrated a dose-dependent protective effect against EtOH/PA-induced injury, as evidenced by improved cell viability, reduced lipid accumulation, and decreased apoptosis (Fig. 2D-2G, Fig. S2D). Consistent with the in vivo findings, EtOH/PA treatment increased the expression of genes involved in lipid metabolism (Srebp1, Acc1, Scd1, Srebp2, Lcn2, and Ldlr) and inflammation (Tnf-α and Il-6), and MgIG treatment effectively reversed these effects (Fig. 2H). Based on these results, we selected 0.25 mg/mL as the optimal MgIG concentration for subsequent in vitro experiments.

MgIG protects ethanol-induced hepatocyte injury in a cell model.

(A) Volcano plot analysis showing differentially expressed genes between the EOH group and the Ctrl group after RNA-seq in the liver of mice. (B) Volcano plot analysis showing differentially expressed genes between the EtOH+M and the EtOH group after RNA-seq in liver of mice. (C) The top 5 regulated pathways (both up- and down-regulated) and the top 3 genes within each pathway are shown (EtOH+M vs EtOH).. (D) Changes in AML-12 cell viability, apoptosis, and Nile Red staining signals after ethanol/PA treatment, with or without co-treatment with different MgIG doses (EtOH+M) (0, 0.1, 0.25, 0.5, and 1 mg/mL) (n = 4). (E) Representative images of Nile Red staining in AML-12 cells treated with ethanol/PA, with or without co-treatment with different MgIG doses. (F)Quantification of triglyceride (TG) and total cholesterol (TC) levels in the in the culture supernatant of AML-12 cells treated with EtOH/PA in the presence or absence of increasing concentrations of MgIG (n = 4). (G-H) Changes in mRNA expression of lipid metabolism genes (Srebp1, Acc1,Scd1, Srebp2, Lcn2, and Ldlr) and systemic inflammation markers (Tnf-α and Il-6) in AML-12 cells treated with ethanol/PA, with or without co-treatment with different MgIG doses. Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001. Scale bar: 20 μm.

In line with the in vivo observations, Idi1 expression was significantly increased in AML-12 cells following EtOH/PA treatment, and this effect was attenuated by MgIG treatment (Fig. 3A and S3A-3C). As shown in Fig. 3B and 3C, transfection with siRNA and plasmid effectively decreased or increased Idi1 mRNA levels without affecting cell viability, respectively. Knockdown of Idi1 significantly ameliorated EtOH/PA-induced cell injury, as evidenced by reduced apoptosis, inflammatory cytokine production, and lipid accumulation. In contrast, Idi1 overexpression tended to exacerbate these pathological changes (Fig. 3D-3H, Fig. S3). Although the effects of Idi1 overexpression on apoptosis and inflammatory cytokines did not reach statistical significance in Western blot analyses, Idi1 overexpression markedly attenuated the hepatoprotective effects of MgIG (Fig. 3E, Fig. S3A) . One possible explanation is that Idi1 functions as a permissive factor in EtOH/PA-induced hepatocellular injury, rather than acting as a sole or rate-limiting determinant. In this context, modulation of Idi1 may be necessary to facilitate lipid metabolic reprogramming and stress responses, but is not sufficient on its own to fully dictate cell fate decisions such as apoptosis or survival. This interpretation is consistent with the multifactorial nature of ALD, which involves the coordinated interplay of oxidative stress, inflammatory signaling, and metabolic dysregulation 5,6. Given that MgIG has been reported to exert broad anti-inflammatory and antioxidant effects13, it is likely that its hepatoprotective actions are mediated through multiple parallel pathways, with Idi1 representing one important, but not exclusive, target. Taken together, these findings suggest that MgIG protects against ethanol-induced hepatocyte injury, at least in part, through the modulation of IDI1.

IDI1 is involved in MgIG-mediated hepatocyte protection against ethanol.

(A) Quantitative PCR validation of RNA-seq results revealed changes in Idi1 gene expression in AML-12 cells treated with ethanol/PA, with or without 0.25 mg/mL MgIG co-treatment (EtOH/PA and EtOH/PA+M) (n = 4). (B) Quantitative PCR results confirmed the knockdown or overexpression efficiency of Idi1 genes by siRNA or Idi1 plasmid in AML-12 cells. (C) The changes in AML-12 cell viability following Idi1 siRNA or Idi1 plasmid transfection (24 h) were also assessed (n = 4). (D) Changes in cell viability and apoptosis ratios were assessed in ethanol/PA-treated AML-12 cells, with or without 0.25 mg/mL MgIG, following Idi1 knockdown/overexpression (n = 4). (E, F) Western blot results for TNF-α, IL-6, Bax, and Bcl-2 and cell supernatant results for TNF-α and IL-6 in AML-12 cells treated with ethanol/PA (EtOH/PA) and ethanol/PA + MgIG (EtOH/PA+M), with or without Idi1 knockdown/overexpression. Numbers above the lanes indicate the mean relative density normalized to the loading control for each group (n = 3). (G, H) Nile Red staining area (%) with corresponding representative cell staining images. Data are expressed as mean ± SD. For Western blot quantification: *P < 0.05, **P < 0.01, ***P < 0.001. Scale bar: 20 μm.

MgIG directly binds to HSD11B1

To identify potential direct binding partners of MgIG, we initially performed molecular docking simulations between MgIG and IDI1. However, the resulting Glide score of -2.74 indicated a lack of favorable binding interactions, which implied that there should be an immediate binding protein in the upstream of IDI1. To identify potential upstream regulators of Idi1 expression, we utilized the ULM within the DecoupleR package to analyze transcription factor activity. This analysis identified SREBP2 as the most significantly affected transcription factor (Fig. 4A). We then expanded our search to include upstream regulators of IDI1 identified using the STRING database. Among these proteins, HSD11B1 exhibited the highest binding affinity for MgIG, with a Glide score of -8.75 (Fig. 4B). Given the homology between human and mouse Hsd11b1 and the need for future translational research, we focused on validating the interaction between human HSD11B1 and MgIG. We conducted 100 ns MD simulations for Compound-HSD11B1 (MgIG-HSD11B1 binding in physiological condition) and EtOH-HSD11B1 (MgIG-HSD11B1 binding in alcoholic condition), with free HSD11B1 as a control. The results revealed that HSD11B1 exhibited high flexibility and dynamic motion in its unbound state but became significantly more rigid and stable upon binding to MgIG, particularly at residues 219–233 (Fig. 4C-4E). This structural stabilization was further supported by the radius of gyration curves, which indicated a more compact conformation upon binding (Fig. S5 and 5B). Further analyses, including PCA and DCCM, demonstrated alterations in motion direction, dynamic patterns, and residue correlations. Specifically, upon binding, HSD11B1 exhibited reduced motion amplitude and weaker residue correlations, with its dynamic patterns becoming more disordered (Fig. S5C-5E). In the Compound-HSD11B1 system (Fig. 4E), key interactions included hydrogen bonds (Tyr177, Tyr183), a salt bridge (Lys187) and hydrophobic interactions (Leu126, Leu217, Ala223, Ala226, and Ile230). In contrast, the EtOH-HSD11B1 system (Fig. 4F) exhibited hydrogen bonds (Thr124, Ser170, Tyr183, Leu217, and Arg269) along with an additional salt bridge (Tyr183 and Arg269). Notably, the EtOH-HSD11B1 system demonstrated stronger hydrogen bonding and more favorable binding free energy compared to the Compound-HSD11B1 system (Fig. 4G and S5F), suggesting enhanced stability and binding affinity in an ethanol environment. Based on molecular docking and MD results, we further validated the binding between MgIG and the human full-length wild-type (WT) HSD11B1 protein as well as its site-directed mutants (Tyr177, M1; Tyr183, M2; Lys187, M3) using MST. The Kd value of the WT protein was 6.35 μM (Fig. 4H), while those of M1, M2, and M3 were 48.6 μM, 11.5 μM, and 135.6 μM, respectively (Fig. 4I). These data indicate that MgIG primarily exerts its anti-ALD effect by inhibiting HSD11B1 through the critical Lys187 site.

HSD11B1 is the direct binding protein of MgIG for the protection of ethanol-induced hepatocytes injury.

(A) Bar chart displaying the top 10 upregulated and downregulated transcription factor activity scores in the EtOH+M group compared to the EtOH group. (B) The glide score of MgIG binding to the protein structure as determined by molecular docking analysis. (C, D) RMSD and RMSF analysis of the three systems: APO-HSD11B1 (blue) represents unbound HSD11B1 in a physiological saline system, Compound-HSD11B1 (red) represents HSD11B1 bound to MgIG in a physiological saline system, and EtOH-HSD11B1 (green) represents HSD11B1 bound to MgIG in a 0.1 mg/mL ethanol solvent system. (E, F) Molecular modeling analysis of MgIG binding at the HSD11B1 domain in normal saline and ethanol systems. Left: Cartoon view of MgIG at the HSD11B1 binding site. Right: Close-up surface view of MgIG at the HSD11B1 binding sites. (G) Hydrogen bond analysis of HSD11B1-MgIG interactions in normal saline and ethanol systems. (H, I) The microscale thermophoresis (MST) assay demonstrated direct binding between varying doses of MgIG and human HSD11B1 protein at residues 187. WT: wild-type HSD11B1; M1, M2, M3: point mutations at Tyr177, Tyr183, and Lys187, respectively.

To further investigate the functional significance of this interaction, we modulated Hsd11b1 expression in AML-12 cells using siRNA- and plasmid-mediated knockdown and overexpression, respectively. As shown in Fig. 5A-5C, transfection with siRNA and plasmid effectively decreased or increased Hsd11b1 mRNA levels without affecting cell viability, respectively. Knockdown of Hsd11b1 significantly attenuated EtOH/PA-induced inflammation, apoptosis, and lipid accumulation, even in the absence of MgIG treatment. Conversely, overexpression of Hsd11b1 exacerbated these effects. Importantly, MgIG treatment partially reversed the detrimental effects of Hsd11b1 overexpression (Fig. 5D-5F, Fig. S4C, 4F, 4G). To further investigate whether the binding of MgIG to HSD11B1 affects its enzymatic activity, we added different concentrations of MgIG (0.1, 0.25, and 0.5 mg/mL) to the cellular model. ELISA results showed that HSD11B1 activity was significantly elevated in the ALD group, whereas increasing concentrations of MgIG led to a dose-dependent reduction in HSD11B1 activity (Fig. 5G).Given the low basal activity under normal conditions, we further examined cortisol levels in the supernatant of AML-12 cells overexpressing Hsd11b1, with or without MgIG co-treatment (Fig. 5H). These findings suggested that MgIG exerted its protective effects against EtOH/PA-induced hepatocyte injury, at least in part, by directly binding to and modulating the activity of HSD11B1.

HSD11B1 is involved in MgIG-mediated hepatocyte protection against ethanol.

(A) Quantitative PCR validation of RNA-seq results revealed changes in Hsd11b1 gene expression in AML-12 cells treated with ethanol/PA, with or without 0.25 mg/mL MgIG co-treatment (EtOH/PA and EtOH/PA+M) (n = 4). (B, C) Quantitative PCR confirmed the knockdown efficiency of Hsd11b1 (siRNA) and the overexpression efficiency of Hsd11b1(plasmid) in AML-12 cells, and cell viability changes were assessed 48 h after transfection (n = 4). (D) Nile Red staining area (%) with corresponding representative cell staining images (n=4). (E, F) Western blot results for TNF-α, IL-6, Bax, and Bcl-2 and cell supernatant results for TNF-α and IL-6 in AML-12 cells treated with ethanol/PA (EtOH/PA) and ethanol/PA + MgIG (EtOH/PA+M), with or without Hsd11b1 knockdown/overexpression. Numbers above the lanes indicate the mean relative density normalized to the loading control for each group (n = 3). (G,H) Impact of MgIG on Hsd11b1 Activity. Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001. Scale bar: 20 μm.

MgIG protects hepatocyte partially through the HSD11B1–SREBP2–IDI1 axis

To investigate the relationship between SREBP2 and HSD11B1, we conducted co-IP experiments, which revealed a direct interaction between the precursor form of SREBP2 (p-SREBP2) and HSD11B1 (Fig. S4E-4G). This interaction appeared to be reduced following MgIG treatment. (Fig. 6A and 6B). To further explore this interaction, we modulated Hsd11b1 expression in EtOH/PA induced AML-12 cells with or without MgIG treatment (Fig. 6C-6D, Fig. S6). Knockdown of Hsd11b1 reduced nuclear translocation of SREBP2 (n-SREBP2), while Hsd11b1 overexpression promoted the accumulation of n-SREBP2, an effect further enhanced by the EtOH/PA treatment. These findings suggest that HSD11B1 may regulate the processing and nuclear translocation of SREBP2 in in vivo ALD model. Immunofluorescent analysis confirmed these observations (Fig. 6E). As shown in Fig. 6F, the co-IP results indicated that HSD11B1 also interacted with its downstream protein IDI1. In addition, the dual-luciferase reporter assay demonstrated that Srebp2 positively regulates Idi1 expression (Fig. 6G). In in vivo experiments, it was confirmed that in normal liver tissue, the expression of Srebp2 and Idi1 followed a similar trend in response to overexpression or knockdown of Hsd11b1 (Fig. 6H and 6I). Knockdown of Srebp2 resulted in a decrease in Idi1 expression, without affecting Hsd11b1 levels. Conversely, neither knockdown nor overexpression of Idi1 influenced the expression of the upstream genes Hsd11b1 or Srebp2. In liver tissue from ALD, the expression changes of upstream and downstream genes upon overexpression or knockdown of Hsd11b1 or Idi1 mirrored those seen in normal liver tissue. However, Srebp2 knockdown induced a negative feedback effect, reducing Hsd11b1 expression, which was not observed in normal liver tissue (Fig. 6J and 6K).

MgIG exerts its protective effect via the HSD11B1-SREBP2-IDI1 axis in ALD model.

(A, B) Co-IP was used to verify the direct binding between HSD11B1 and SREBP2 with or without MgIG treatment. (C, D) Alterations in protein levels of HSD11B1, p-SREBP2, n-SREBP2, and IDI1 in AML-12 cells induced by EtOH/PA, following knockdown or overexpression of Hsd11b1, with and without MgIG treatment. Numbers above the lanes indicate the mean relative density normalized to the loading control for each group (n = 3). (E) Immunofluorescent staining was conducted to visualize the distribution and expression of SREBP2 (red) in EtoH/PA-induced AML-12 cells, with or without MgIG, following Hsd11b1 knockdown or overexpression. (F) Co-IP was used to verify the direct binding between HSD11B1 and IDI1. (G) Effects of Srebp2 on Idi1 transcriptional regulation were measured by luciferase assays in AML-12 and 293T cell lines. Idi1-wild-type (WT) or Idi1-mutant (Mut), plasmids with WT promoter cDNA clone of Idi1 or with mutant promoter cDNA clone plasmid; pRL-TK, an internal control reporter plasmid. (H, I) The expression levels of Hsd11b1, Srebp2, and Idi1 in normal liver were measured following the knockdown of Hsd11b1, Srebp2, and Idi1, or the overexpression of Hsd11b1 and Idi1, respectively (n = 4). (J, K) The expression levels of Hsd11b1, Srebp2, and Idi1 in ALD liver were measured following the knockdown of Hsd11b1, Srebp2, and Idi1, or the overexpression of Hsd11b1 and Idi1, respectively (n = 5). Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001. ****P < 0.0001. Scale bar: 10 μm.

To further investigate the roles of HSD11B1, SREBP2, and IDI1 in the in vivo ALD model, we used AAV8-mediated shRNA delivery to knock down their expression or employed overexpression plasmids to increase their expression specifically in hepatocytes. As shown in Fig. S6A-6C, knockdown or overexpression of Hsd11b1 or Idi1 in mice fed a normal control diet did not result in significant changes in liver histology, lipid accumulation, or serum ALT and AST levels (Fig. S7). However, in the ALD model, knockdown of Hsd11b1, Srebp2, or Idi1 attenuated ethanol-induced liver injury, as evidenced by improved histological NAS scores, reduced steatosis, and decreased inflammation. MgIG treatment further enhanced these beneficial effects. Conversely, overexpression of Hsd11b1 or Idi1 abolished the therapeutic effects of MgIG on ethanol-induced liver injury (Fig. 7A-7F and S8). Interestingly, modulation of Idi1 expression did not affect the expression of Hsd11b1 or Srebp2, suggesting that IDI1 acts downstream of HSD11B1 and SREBP2. In contrast, modulation of Hsd11b1 expression altered the levels of n-SREBP2 and IDI1 (Fig. S8E-H), confirming that HSD11B1 regulates the SREBP2-IDI1 pathway. Collectively, these data indicate that MgIG protects against ALD, at least in part, by modulating the HSD11B1-SREBP2-IDI1 axis.

MgIG alleviates ALD-induced liver injury via the HSD11B1-SREBP2-IDI1 axis.

(A-D) Representative liver H&E and Oil Red O staining results from ALD mice with Hsd11b1, Srebp2, or Idi1 knockdown or overexpression, with and/or without MgIG co-treatment. Changes in quantitative NAS (NAFLD activity score) and Oil Red staining (area %) were calculated and analyzed (n = 5). (E-F) Changes of serum ALT and TNF-α from ALD mice with Hsd11b1, Srebp2, or Idi1 knockdown or overexpression, with and/or without MgIG co-treatment (n = 5). (G) Alterations in protein levels of HSD11B1, p-SREBP2, n-SREBP 2, and Idi1 in ALD mice, following knockdown or overexpression of Hsd11b1, with and without MgIG co-treatment. Numbers above the lanes indicate the mean relative density normalized to the loading control for each group (n = 3). Data are expressed as mean ± SD. *P < 0.05, **P < 0.01, ***P < 0.001, ****P < 0.0001. Scale bar: 50 μm.

Discussion

While previous research using a zebrafish model demonstrated that MgIG alleviates alcohol-induced liver injury by modulating lipid metabolism-related gene expression 18, the precise molecular mechanisms and direct targets of MgIG remained unclear. This lack of mechanistic understanding hindered the development of optimized therapeutic strategies for ALD. In this study, we provide compelling evidence that MgIG effectively ameliorates key features of ALD, including hepatic steatosis, inflammation, and apoptosis, in both in vivo and in vitro models. Our findings shed light on the complex interplay of molecular pathways involved in ALD pathogenesis and highlight the therapeutic potential of targeting the HSD11B1-SREBP2-IDI1 axis.

Our RNA sequencing analysis identified IDI1 as a key player in ALD pathogenesis and a critical mediator of MgIG’s hepatoprotective effects. IDI1, an enzyme in the mevalonate pathway, is involved in the biosynthesis of isoprenoids, which are essential for various cellular processes, including cholesterol synthesis. Dysregulation of cholesterol metabolism is a hallmark of ALD, contributing to the accumulation of lipids in the liver. Our findings demonstrate that Idi1 expression is significantly upregulated in the livers of mice subjected to the NIAAA model of ALD, suggesting that increased IDI1 activity may contribute to the development of hepatic steatosis. Genetic manipulation of Idi1 expression further confirmed its role in ALD. Specifically, Idi1 knockdown protected against alcohol-induced liver injury, an effect further enhanced by MgIG treatment. This suggests that reducing IDI1 activity can ameliorate the detrimental effects of alcohol on the liver and that MgIG may exert its therapeutic benefits, at least in part, by suppressing IDI1. Conversely, Idi1 overexpression abolished the therapeutic benefits of MgIG, both in vivo and in vitro, highlighting the importance of IDI1 in mediating MgIG’s effects. These findings are consistent with recent reports highlighting the role of IDI1 in hepatic cholesterol accumulation and lipid toxicity 40 41 and its involvement in hepatocellular carcinoma progression via inhibition of the cGAS-STING pathway 9. Furthermore, our study identified SREBP2, a master regulator of lipid metabolism, as an upstream regulator of IDI1. SREBP2 belongs to a family of transcription factors that control the expression of genes involved in cholesterol and fatty acid biosynthesis. SREBP2 has been implicated in various aspects of liver pathology, including NLRP3 inflammasome activation 42, lipid accumulation 43, liver cancer progression 44, with its target protein IDI1 upregulated in parallel 30. Our findings demonstrate that both SREBP2 and IDI1 are upregulated in response to EtOH/PA treatment and that MgIG effectively inhibits their expression, consistent with the notion that SREBP2 contributes to the development of MASLD 45. The identification of SREBP2 as a key regulator of IDI1 in the context of ALD provides a mechanistic link between lipid metabolism and the pathogenesis of this disease.

To identify the direct molecular target of MgIG, we employed a combination of molecular docking, MD, MST analysis, and genetical manipulation studies. These approaches converged on HSD11B1, a key enzyme in glucocorticoid metabolism, as a high-affinity binding partner of MgIG. HSD11B1 catalyzes the conversion of inactive cortisone to active cortisol in the liver, thereby increasing intracellular glucocorticoid levels. Glucocorticoids are steroid hormones that play a critical role in regulating glucose and lipid metabolism, and their dysregulation has been implicated in the development of metabolic disorders, including type 2 diabetes 46. As a potential inhibitor of HSD11B1 47, GL can improve patients’ insulin and lipid levels 48. In addition, the increased expression of Hsd11b1 enhances the enzymatic reducing activity, promoting a fat-forming phenotype in cell models through elevated cortisol levels 49,50. Meanwhile, Hsd11b1 deficiency prevents hepatic steatosis in high-fat diets-fed mice 51. Our findings demonstrate that MgIG directly binds to the Lys187 of HSD11B1 and that modulation of Hsd11b1 expression in hepatocytes significantly influences the development of ALD.

While some studies have suggested a potential pro-fibrotic role for HSD11B1 inhibition 8, our findings, along with those of other recent studies 7,51,52, support a protective role for Hsd11b1 knockdown in the context of alcoholic liver injury. These discrepancies may be attributed to differences in experimental models and the specific cell types targeted. For instance, the study by Zou et al 8 examined the effects of global Hsd11b1 deficiency, which could trigger compensatory activation of the hypothalamic-pituitary-adrenal axis or paracrine regulatory mechanisms, potentially affecting the pro-fibrotic response. In contrast, our study focused on hepatocyte-specific Hsd11b1 knockdown, which may avoid these confounding factors. Importantly, our study provides evidence for a novel HSD11B1-SREBP2-IDI1 axis in the pathogenesis of ALD. We demonstrate that HSD11B1 regulates the processing and nuclear translocation of SREBP2, which in turn controls the expression of IDI1. Notably, this is consistent with previous studies showing that increased SREBP2 expression and nuclear translocation activate the NLRP3 inflammasome and the mevalonate pathway, thereby promoting inflammation and tumor progression 53,54. This regulatory axis appears to be a key target of MgIG’s therapeutic effects. By directly binding to HSD11B1, MgIG may inhibit its activity, leading to reduced SREBP2 activation and subsequent downregulation of IDI1. This, in turn, could contribute to the observed improvements in hepatic steatosis, inflammation, and apoptosis 55–57.

This study provides mechanistic evidence that MgIG directly targets HSD11B1 and modulates the HSD11B1–SREBP2–IDI1 axis to attenuate ALD. However, several limitations should be acknowledged. First, our findings are derived from preclinical mouse models and hepatocyte systems, and pharmacokinetics, biodistribution, and long-term safety of MgIG remain to be comprehensively evaluated in larger and more diverse populations. Second, although molecular docking and thermophoresis confirmed direct binding of MgIG to HSD11B1, high-resolution structural studies such as X-ray crystallography or cryo-electron microscopy are needed to delineate the precise binding interface and conformational changes. Third, other signaling pathways potentially influenced by MgIG have not been systematically explored and may contribute to its therapeutic effects. Future work should focus on validating these findings in human tissues, optimizing MgIG dosing strategies, and conducting multicenter clinical trials to assess its translational potential and establish HSD11B1 as a druggable target for precision therapy in ALD.